---
title: "Respondent demographics"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, dpi = 170)
```

```{r libraries}
library(tidyverse)
library(cwi)
library(janitor)
library(camiller)
source("../utils/plot_utils.R")
label_col <- c("#EDEEF2")
```

```{r paths}
path <- "../survey_data/01032023/"
plot_path <- "../distro/"

age_labels <- tibble(age = c("age00_29", "age30_49", "age50_99", "Total"),
                     label = c("Under 30", "30-49", "50 and over", "Total")) %>% 
  mutate(label = as.factor(label) %>% 
           fct_relevel(., "Total", "Under 30", "30-49", "50 and over"))

read <- read_csv(paste(path, "clean.csv", sep = "")) %>% 
  rename(age = big_age_band)
```

Current number of respondents (blanks removed) as of January 3, 2023.

```{r count}
read %>% 
  select(survey) %>% 
  group_by(survey) %>% 
  count() %>% 
  adorn_totals()
```

**I'm going to stop disaggregating by survey type so we can focus on disaggregating by other metrics, like age, gender, or nationality**

## Age

```{r age}
#read %>% select(small_age_band) %>% filter(!is.na(small_age_band)) %>% count()

age <- read %>%
  select(small_age_band) %>% 
  group_by(small_age_band) %>%
  count() %>% 
  ungroup() %>% 
  mutate(small_age_band = as.factor(small_age_band) %>% 
           fct_relevel(., "Under 18")) %>% 
  mutate(pct = n / 2028)

age %>%
  filter(!is.na(small_age_band)) %>% 
  ggplot(aes(x = small_age_band, y = pct)) +
  geom_col() +
  geom_text(aes(label = scales::percent(pct, accuracy = 1)), vjust = 1.2, color = label_col) +
  scale_y_continuous(expand = expansion(mult = c(.01, .1))) +
  labs(title = "Share of respondents by age group", x = NULL, y = NULL) +
  theme(axis.text.y = element_blank())
```

This time around, I'll group ages into 0-29, 30-49, and 50+

## Gender x age

Across all age groups, more women than men responding, with greatest disparity in 30-49 range. Keep that in mind as we look at these age-based breakdowns later.

```{r eval = F}
gender_age_totals <- read %>% 
  select(gender, age) %>% 
  filter(!is.na(age), !is.na(gender)) %>% 
  group_by(gender, age) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(read %>%
              select(gender, age) %>% 
              filter(!is.na(age), !is.na(gender)) %>% 
              select(-age) %>% 
              mutate(age = "Total") %>% 
              group_by(gender, age) %>% 
              count() %>% 
              ungroup()) %>% 
  bind_rows(read %>%
              select(gender, age) %>% 
              filter(!is.na(age), !is.na(gender)) %>% 
              select(-gender) %>% 
              mutate(gender = "Total") %>% 
              group_by(gender, age) %>% 
              count() %>% 
              ungroup()) %>% 
  add_row(age = "Total", gender = "Total", n = 2005) %>% 
  group_by(age) %>% 
  calc_shares(group = gender, denom = "Total", value = n) %>% 
  mutate(gender = as.factor(gender) %>% 
           fct_relevel(., "Woman", "Man", "Transgender & NB", "Total"))

gender_age_totals %>% 
  left_join(age_labels, by = "age") %>% 
  mutate(label = fct_rev(label)) %>% 
  filter(!is.na(share)) %>% 
  ggplot(aes(x = share, y = label, group = gender)) +
  geom_col(aes(fill = gender), width = .8, position = position_dodge()) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), color = "grey20") +
  scale_fill_manual(values = c(cb_pal[4], cb_pal[1], cb_pal[8])) +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(x = NULL, y = NULL, title = "Respondents by gender and age")
```

```{r gender}
gender <- read %>% 
  select(gender, age) %>% 
  group_by(age, gender) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(gender = as.factor(gender) %>% 
           fct_relevel(., "Woman", "Man", "Transgender & NB"))
gender %>% 
  left_join(age_labels, by = "age") %>% 
  filter(!is.na(gender), !is.na(age), gender != "Opt out") %>% 
  ggplot(aes(x = label, y = n, group = gender)) +
  geom_col(aes(fill = gender), width = .8, position = position_dodge(.9)) +
  geom_text(aes(label = n), position = position_dodge(.9), vjust = -.2, color = "grey20") +
  scale_fill_manual(values = c(cb_pal[4], cb_pal[1], cb_pal[8])) +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(expand = expansion(mult = c(.01, .1))) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank()) +
  labs(x = NULL, y = NULL, title = "Number of respondents by gender and age range")
```

## Town of residence

```{r}
library(sf)

town <- read %>%
  select(name = residence_town) %>% 
  group_by(name) %>% 
  count()

town_sf <- cwi::town_sf %>% 
  left_join(town, by = "name") %>% 
  mutate(brk = cut(n, breaks = c(0, 10, 20, 40, 100, Inf), labels = c("1 to 10", "11 to 20", "21 to 40", "41 to 100", "101 and over"), right = T))

labels_sf <- town_sf %>%
  mutate(cent = map(geometry, polylabelr::poi),
         cx = map_dbl(cent, 1),
         cy = map_dbl(cent, 2),
         geometry = map2(cx, cy, ~st_point(x = c(.x, .y))) %>%
           st_sfc() %>%
           st_geometry()) %>%
  select(-cent:-cy) %>%
  st_set_crs(st_crs(town_sf))

ggplot() +
  geom_sf(data = town_sf %>% filter(is.na(n)), fill = "grey90", size = .25, show.legend = F) +
  geom_sf(data = town_sf %>% filter(!is.na(n)), aes(fill = brk), size = .25, show.legend = F) +
  geom_sf_text(data = labels_sf, aes(geometry = geometry, label = scales::comma(n, accuracy = 1)), color = "white", size = 2.75) +
  coord_sf(ndiscr = 0) +
  labs(title = "Number of respondents by town of residence", caption = "Not shown: 55 respondents who are not residents of Connecticut", x = NULL, y = NULL) +
  scale_fill_manual(values = rev(gradient_pal))
```

## Ethnicity x gender x age

Slightly lower shares of older adults identifying as Latino

```{r ethnicity}
gender_age_totals <- read %>% 
  select(gender, age) %>% 
  group_by(gender, age) %>% 
  count()

ethnicity <- read %>% 
  select(latino, gender, age) %>% 
  group_by(latino, gender, age) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(gender_age_totals %>% mutate(latino = "Total")) %>% 
  group_by(age, gender) %>% 
  calc_shares(group = latino, denom = "Total", value = n) %>% 
  ungroup()

ethnicity %>% 
  filter(!is.na(share), !is.na(age), latino == "Yes", !is.na(gender), !gender %in% c("Transgender & NB", "Opt out"), !is.na(age))
  
  
  # ggplot(aes(x = age, y = share, group = gender)) +
  # geom_col(aes(fill = gender), width = .8, position = position_dodge(.9)) +
  # geom_text(aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), vjust = 1.2) +
  # scale_fill_manual(values = c(cb_pal[4], cb_pal[1])) +
  # labs(title = "Share of respondents who identify as Latino/Latina/Latinx", x = NULL, y = NULL, caption = "Transgender & NB dropped due to low counts") +
  # theme(axis.text.y = element_blank(),
  #       legend.position = "bottom")
```

## Place of birth x age

Younger and older people more likely to be born in the US/PR. I am surprised at the diversity in the 30-49 crowd.

```{r pob}
# read %>% select(place_of_birth) %>% 
#   group_by(place_of_birth) %>% 
#   count() %>% 
#   ungroup() %>% 
#   mutate(share = n / 2043) %>% 
#   mutate(share = scales::percent(share, accuracy = 1)) %>% 
#   knitr::kable()

age_totals <- read %>% 
  select(pob = place_of_birth, age) %>% 
  filter(!is.na(age), !is.na(pob)) %>% 
  select(-pob) %>% 
  group_by(age) %>% 
  count()

pob <- read %>% 
  select(pob = place_of_birth, age) %>% 
  group_by(pob, age) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(age_totals %>% mutate(pob = "Total")) %>% 
  group_by(age) %>% 
  calc_shares(group = pob, denom = "Total", value = n) %>% 
  ungroup()

pob %>%
  left_join(age_labels, by = "age") %>% 
  mutate(label = fct_rev(label)) %>% 
  mutate(pob = str_to_title(pob),
         pob = if_else(pob == "Usa", "USA", pob),
         pob = as.factor(pob) %>% 
           fct_relevel(., "USA", "Puerto Rico", "Mexico", "Ecuador", "Other")) %>% 
  ggplot(aes(x = share, y = label, group = label)) +
  geom_col(aes(fill = pob), width = .8, position = position_stack(.9)) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), position = position_stack(.5), color = "#EDEEF2") +
  geom_text(data = . %>% filter(label == "Under 30"), aes(label = pob, color = pob), position = position_stack(.5), vjust = -5.6, size = 3.5) +
  theme(legend.position = "none",
        axis.text.x = element_blank()) +
  scale_fill_manual(values = gradient_pal) +
  scale_x_continuous(expand = expansion(mult = c(.01, 0))) +
  scale_color_manual(values = gradient_pal) +
  labs(x = NULL, y = NULL, title = "Respondents by age and place of birth",
       caption = "Puerto Rico and USA may not be mutually exclusive")
```

## Language spoken at home x age

Pretty even language split among older adults.

```{r fig.width = 5, lang_at_home}
lang_at_home <- read %>% 
  select(language) %>% 
  mutate(language = if_else(is.na(language), "Other", language)) %>% 
  group_by(language) %>%
  count() %>% 
  ungroup() %>% 
  mutate(share = n / 1961)

lang_at_home2 <- read %>%
  select(language, age) %>%
  mutate(language = if_else(is.na(language), "Other", language)) %>%
  group_by(age, language) %>%
  count() %>%
  ungroup() %>%
  bind_rows(age_totals %>% mutate(language = "Total")) %>%
  group_by(age) %>%
  calc_shares(group = language, denom = "Total", value = n) %>%
  ungroup()

#read %>% select(language) %>% filter(!is.na(language)) %>% count()
# 
# read %>%
#   select(language) %>% 
#   filter(!is.na(language)) %>%
#   group_by(language) %>% 
#   count() %>% 
#   mutate(share = n / 1961) %>% 
#   mutate(share = scales::percent(share, accuracy = 1)) %>% 
#   knitr::kable()

lang_at_home %>% 
  mutate(language = str_wrap(language, width = 13)) %>% 
  ggplot(aes(x = share, y = reorder(language, share))) +
  geom_col(aes(fill = language), width = .8, show.legend = F) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col) +
  scale_x_continuous(expand = expansion(mult = c(.01, 0))) +
  theme(axis.text.x = element_blank()) +
  scale_fill_manual(values = gradient_pal) +
  labs(x = NULL, y = NULL, title = "Share of respondents by language spoken at home")
```

## Internet-enabled devices and internet at home x age

I'm kind of shocked at the under-30 lack of device/internet, but not at the notable increase in lack of internet in older age groups; lack of device corresponds with lack of internet.

```{r internet}
internet <- read %>%
  select(web_at_home, age) %>% 
  group_by(web_at_home, age) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(age_totals %>% mutate(web_at_home = "Total")) %>% 
  group_by(age) %>% 
  calc_shares(group = web_at_home, denom = "Total", value = n)

internet %>%
  filter(web_at_home == "No", !is.na(age))

# 
#   ggplot(aes(x = age, y = share)) +
#   geom_col(width = .5) +
#   geom_text(aes(label = scales::percent(share, accuracy = 1)), vjust = 1.2) +
#   labs(x = NULL, y = NULL, title = "Respondents without internet at home, by age") +
#   theme(axis.text.y = element_blank())
```

```{r device}
device <- read %>%
  select(web_device, age) %>% 
  group_by(web_device, age) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(age_totals %>% mutate(web_device = "Total")) %>% 
  group_by(age) %>% 
  calc_shares(group = web_device, denom = "Total", value = n)

device %>%
  filter(web_device == "No", !is.na(age)) 

# 
#   ggplot(aes(x = age, y = share)) +
#   geom_col(width = .5) +
#   geom_text(aes(label = scales::percent(share, accuracy = 1)), vjust = 1.2) +
#   labs(x = NULL, y = NULL, title = "Respondents without an internet-enabled device, by age") +
#   theme(axis.text.y = element_blank())
```

```{r neither}
neither <- read %>%
  select(web_device, web_at_home, age) %>% 
  mutate(neither = if_else(web_device == "No" & web_at_home == "No", "Neither", "One or both")) %>% 
  group_by(neither, age) %>% 
  count() %>% 
  ungroup() %>%
  filter(!is.na(neither), !is.na(age)) %>% 
  bind_rows(age_totals %>% mutate(neither = "Total")) %>% 
  group_by(age) %>% 
  calc_shares(group = neither, denom = "Total", value = n)

neither
```

## Registered voter x age x gender

This is pretty typical nationwide.

```{r voter}
voter <- read %>% 
  select(registered_voter, gender, age) %>% 
  group_by(registered_voter, gender, age) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(gender_age_totals %>% mutate(registered_voter = "Total")) %>% 
  group_by(age, gender) %>% 
  calc_shares(group = registered_voter, denom = "Total", value = n) %>% 
  ungroup()

voter %>% 
  filter(!is.na(share), !is.na(age), registered_voter == "Yes", !is.na(gender), !gender %in% c("Transgender & NB", "Opt out"), !is.na(age)) %>% 
  left_join(age_labels, by = "age") %>% 
  ggplot(aes(x = label, y = share, group = gender)) +
  geom_col(aes(fill = gender), width = .8, position = position_dodge(.9)) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), vjust = 1.2, color = label_col) +
  scale_fill_manual(values = c(cb_pal[4], cb_pal[1])) +
  labs(title = "Share of respondents who are registered to vote, by gender", x = NULL, y = NULL, caption = "Transgender & NB dropped due to low counts") +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(expand = expansion(mult = c(.01, 0))) +
  theme(axis.text.y = element_blank(),
        legend.position = "bottom")
  
```

## Other demographic details

Unsurprisingly, half of the students are younger people, middle aged adults have kids under 18. Few business owners.

```{r person_type}
person_type <- read %>%
  select(person_type, age) %>% 
  group_by(person_type, age) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(age_totals %>% mutate(person_type = "Total")) %>% 
  group_by(age) %>% 
  calc_shares(group = person_type, denom = "Total", value = n) %>% 
  ungroup()

person_type %>% filter(age != "Total")

# 
#   ggplot(aes(x = share, y = label)) +
#   geom_col(width = .8, position = position_dodge(.9)) +
#   geom_text(data = . %>% filter(share >= .11), aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), hjust = 1.2, color = label_col) +
#   geom_text(data = . %>% filter(share < .11), aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), hjust = -.2, color = "black") +
#   facet_grid(cols = vars(person_type)) +
#   scale_fill_manual(values = c(cb_pal[4], cb_pal[1])) +
#   labs(title = "Share of respondents by person type", x = NULL, y = NULL, caption = "Transgender & NB dropped due to low counts") +
#     guides(fill = guide_legend(title = NULL)) +
#   theme(axis.text.x = element_blank(),
#         legend.position = "bottom")
```


