---
title: "News habits"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r}
library(tidyverse)
library(cwi)
library(janitor)
library(camiller)
source("../utils/plot_utils.R")

#Cannot just re-run this! some denoms are hard-coded for non-response, and there's some text mining
```


```{r}
path <- "../survey_data/07182022/"
plot_path <- "../distro/"
```

```{r}
read_english <- read_csv(paste(path, "(English) RJ Latino Communities Reporting Lab Survey (Responses) - Form Responses 1.csv", sep = "")) %>% 
  clean_names()

read_spanish <- read_csv(paste(path, "(Spanish) RJ Latino Communities Reporting Lab Survey (Responses) - Form Responses 1.csv", sep = "")) %>% 
  clean_names()

qhead_eng <- tibble(question = paste("Q", 1:31, sep = ""),
                    label = colnames(read_english))
qhead_spn <- tibble(question = paste("Q", 1:31, sep = ""),
                    label = colnames(read_spanish))

colnames(read_english) <- qhead_eng$question
colnames(read_spanish) <- qhead_eng$question

read_english <- read_english %>% select(-Q1, -Q29) %>% remove_empty("rows")
read_spanish <- read_spanish %>% select(-Q1, -Q29) %>% remove_empty("rows")
```

# News habits

## Media used vs. Media preferred

I broke these into two charts by survey language and age so we can compare what medium they prefer to which they use more easily.

```{r}
response_mode <- tibble(use_mode = as.factor(read_english$Q9),
                        pref_mode = as.factor(read_english$Q11),
                        survey = as.factor("English")) %>% 
  bind_rows(tibble(use_mode = as.factor(read_spanish$Q9),
                   pref_mode = as.factor(read_spanish$Q11),
                   survey = as.factor("Spanish"))) %>% 
  filter(!is.na(pref_mode) & !is.na(use_mode)) %>% 
  mutate(clean_use = if_else(grepl("app|online|noticias", use_mode), "News apps", as.character(use_mode)),
         clean_use = if_else(use_mode %in% c("Medios sociales"), "Social media", clean_use),
         clean_use = if_else(grepl("Amistades|Friends|Familiares", clean_use), "Social circles", clean_use),
         clean_use = if_else(grepl("Correo", clean_use), "Email/newsletters", clean_use),
         clean_use = if_else(grepl("Periódicos", clean_use), "Newspapers", clean_use),
         clean_use = if_else(clean_use == "Textos", "Text message", clean_use)) %>% 
  mutate(clean_pref = if_else(grepl("app|online|noticias|Same", pref_mode), "News apps", as.character(pref_mode)),
         clean_pref = if_else(pref_mode %in% c("Medios sociales"), "Social media", clean_pref),
         clean_pref = if_else(grepl("Amistades|Friends|Familiares", clean_pref), "Social circles", clean_pref),
         clean_pref = if_else(grepl("Correo|Email", clean_pref), "Email/newsletters", clean_pref),
         clean_pref = if_else(grepl("Periódicos", clean_pref), "Newspapers", clean_pref),
         clean_pref = if_else(clean_pref == "Textos", "Text message", clean_pref),
         clean_pref = if_else(clean_pref == "Celular", "Text message", clean_pref)) %>% 
  select(survey, clean_use, clean_pref)

mode_to_plot <- response_mode %>%
  select(survey, mode = clean_use) %>%
  tabyl(mode, survey) %>% 
  adorn_totals("row") %>% 
  mutate(type = "Use") %>% 
  bind_rows(response_mode %>% 
              select(survey, mode = clean_pref) %>% 
              tabyl(mode, survey) %>% 
              adorn_totals("row") %>% 
              mutate(type = "Prefer")) %>% 
  pivot_longer(cols = English:Spanish, names_to = "survey", values_to = "value") %>% 
  group_by(survey, type) %>% 
  calc_shares(group = mode, denom = "Total", value = value)
```

For English language respondents, there's a greater preference than use for Email, Text, and news apps, which I think suggest that people prefer more of a digest style news update. TV and social media are popular, of course. Again, I want to disaggregate this by age in the future.

```{r}
mode_to_plot %>% 
  filter(survey == "English") %>% 
  mutate(share = round(share, 2)) %>% 
  filter(!is.na(share)) %>% 
  ggplot(aes(x = type, y = share, group = mode)) +
  geom_col(aes(fill = type), position = position_dodge(.6), width = .5) +
  geom_text(data = . %>% filter(share <= .05), aes(label = scales::percent(share, accuracy = 1)), vjust = -.2, color = "black") +
  geom_text(data = . %>% filter(share > .05), aes(label = scales::percent(share, accuracy = 1)), vjust = 1.2) +
  facet_wrap(~mode) +
  scale_fill_manual(values = unname(qual_pal[c("violet", "cyan", "pink")])) +
  theme(axis.text.y = element_blank(),
        legend.position = "none") +
  labs(x = NULL, y = NULL, title = "News media preferences and use, English survey")
```

For Spanish language respondents, the strong preference towards TV and social media might be in language availability as well as the content covered in Spanish-language TV and through social circles online. Here it would be interesting to disaggregate by age as well as topics or geographies of interest.

```{r}
mode_to_plot %>% 
  filter(survey == "Spanish") %>% 
  filter(!is.na(share)) %>% 
  ggplot(aes(x = type, y = share, group = mode)) +
  geom_col(aes(fill = type), position = position_dodge(.6), width = .5) +
  geom_text(data = . %>% filter(share <= .05), aes(label = scales::percent(share, accuracy = 1)), vjust = -.2, color = "black") +
  geom_text(data = . %>% filter(share > .05), aes(label = scales::percent(share, accuracy = 1)), vjust = 1.2) +
  facet_wrap(~mode) +
  scale_fill_manual(values = unname(qual_pal[c("violet", "cyan", "pink")])) +
  theme(axis.text.y = element_blank(),
        legend.position = "none") +
  labs(x = NULL, y = NULL, title = "News media preferences and use, Spanish survey")
```

```{r}
pref_lang <- tibble(tv_video = read_english$Q6,
                    radio_audio = read_english$Q7,
                    print = read_english$Q8,
                    survey = as.factor("English")) %>% 
  bind_rows(tibble(tv_video = read_spanish$Q6,
                   radio_audio = read_spanish$Q7,
                   print = read_spanish$Q8,
                   survey = as.factor("Spanish"))) %>% 
  mutate(tv_video = if_else(grepl("Inglés", tv_video), "English", tv_video),
         tv_video = if_else(grepl("Español", tv_video), "Spanish", tv_video),
         tv_video = if_else(grepl("Ambos", tv_video), "Both English and Spanish", tv_video),
         tv_video = if_else(grepl("Otro", tv_video), "Other", tv_video)) %>% 
  mutate(radio_audio = if_else(grepl("Inglés", radio_audio), "English", radio_audio),
         radio_audio = if_else(grepl("Español", radio_audio), "Spanish", radio_audio),
         radio_audio = if_else(grepl("Ambos", radio_audio), "Both English and Spanish", radio_audio),
         radio_audio = if_else(grepl("Otro", radio_audio), "Other", radio_audio)) %>% 
  mutate(print = if_else(grepl("Inglés", print), "English", print),
         print = if_else(grepl("Español", print), "Spanish", print),
         print = if_else(grepl("Ambos", print), "Both English and Spanish", print),
         print = if_else(grepl("Otro", print), "Other", print))

pref_lang_to_plot <- pref_lang %>%
  select(survey, language = tv_video) %>%
  filter(!is.na(language), language != "I don't use this format") %>% 
  tabyl(language, survey) %>% 
  adorn_totals("row") %>% 
  mutate(type = "TV/Video") %>% 
  bind_rows(pref_lang %>% 
              select(survey, language = radio_audio) %>% 
              filter(!is.na(language), language != "I don't use this format") %>%  
              tabyl(language, survey) %>% 
              adorn_totals("row") %>% 
              mutate(type = "Radio/Audio")) %>% 
  bind_rows(pref_lang %>% 
              select(survey, language = print) %>% 
              filter(!is.na(language), language != "I don't use this format") %>%  
              tabyl(language, survey) %>% 
              adorn_totals("row") %>% 
              mutate(type = "Print")) %>% 
  pivot_longer(cols = English:Spanish, names_to = "survey", values_to = "value") %>% 
  group_by(survey, type) %>% 
  calc_shares(group = language, denom = "Total", value = value)
```

With language, again a strong preference towards the survey language and "both." In future focus groups if we can ask people who prefer both why they do, that would be helpful.

```{r}
pref_lang_to_plot %>% 
  filter(!is.na(share)) %>% 
  ggplot(aes(x = language, y = share)) +
  geom_col(aes(fill = language), position = position_dodge(.9), width = .8) +
  geom_text(data = . %>% filter(share > 0.1), aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), vjust = 1.2) +
  geom_text(data = . %>% filter(share <= 0.1), aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), vjust = -.2, color = "grey20") +
  guides(fill = guide_legend(title = NULL)) +
  facet_grid(rows = vars(survey), cols = vars(type), scales = "free_y", switch = "y") +
  scale_fill_manual(values = unname(qual_pal[c("violet", "cyan", "pink", "teal")])) +
  theme(legend.position = "bottom",
        axis.text.x = element_blank(),
        axis.text.y = element_blank()) +
  labs(x = NULL, y = "Survey language", title = "Share of respondents by preferred langauge by mode")
```

Preferred sources is also an open text field. Mining for a word cloud...

```{r}
eng_list <- str_split(read_english$Q10, ",| y | and | or|\\/|  ", simplify = T)
spn_list <- str_split(read_spanish$Q10, ",| y | and | or|\\/|  ", simplify = T)

add_back <- tibble(source = c("FACEBOOK", "GOOGLE", "HARTFORD COURANT", "TELEMUNDO", "WFSB", "TELEFE INTERNATIONAL", "RECORD-JOURNAL", "FACEBOOK", "HARTFORD COURANT", "CT POST", "WTNH", "TELEMUNDO"))
                              
                              
x <- tibble(source = c(spn_list, eng_list)) %>% 
  filter(!is.na(source), source != "") %>% 
  mutate(source = str_to_upper(source)) %>%
  mutate(source = str_trim(source, side = "both")) %>% 
  mutate(source = str_remove(source,  c(" IF AVAILABLE| PRINT EDITION"))) %>% 
  filter(!source %in% c("N", "A", "FACEBOOK GOOGLE", "HARTFORD COURANT TELEMUNDO WFSB 3 TELEFE INTERNATIONAL", "RECORD JOURNAL FACEBOOK", "HARTFORD COURANT CT POST WTNH", "TODO", "TODOS", "UN POCO DE TODO", "USUALLY TELEMUNDO", "NONE")) %>% #will add these back properly below
  mutate(source = if_else(grepl("RECORD|RJ|R-J", source), "RECORD-JOURNAL", source),
         source = if_else(grepl("NBC|CHANNEL 30", source), "NBC", source),
         source = if_else(grepl("FOX", source), "FOX NEWS", source),
         source = if_else(grepl("CHANNEL 8", source), "WTNH", source),
         source = if_else(grepl("CHANNEL 3|CHANEL 3|WFSB", source), "WFSB", source),
         source = if_else(grepl("BREAK", source), "NEWSBREAK", source),
         source = if_else(grepl("LOCAL", source), "LOCAL STATIONS", source),
         source = if_else(grepl("HEARALD", source), "NEW BRITAIN HERALD", source),
         source = if_else(grepl("WAPO", source), "WASHINGTON POST", source),
         source = if_else(grepl("UNIV", source), "UNIVISION", source)) %>% 
  mutate(source = str_trim(source, side = "both")) %>% 
  bind_rows(add_back)

cloud <- x %>% group_by(source) %>% count()
```

```{r}
library(ggwordcloud)

set.seed(13)

ggplot(cloud, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = qual_pal[1], low = qual_pal[7])
```

```{r}
#Denoms are hard-coded so we get share of respondents, not share of responses

eng_geo <- tibble(geo = c(str_split(read_english$Q2, ", ", simplify = T)),
                  survey = "English")
spn_geo <- tibble(geo = c(str_split(read_spanish$Q2, ", ", simplify = T)),
                  survey = "Spanish")

response_geos <- bind_rows(eng_geo, spn_geo) %>% 
  filter(!geo %in% c("", "No", "None", "Yo'u're too biased.  way too liberal.", "PUERTO RICO")) %>% 
  mutate(geo = if_else(geo == "Estatal", "State", geo),
         geo = if_else(geo == "Nacional", "National", geo),
         geo = if_else(grepl("Inter", geo), "International", geo),
         geo = if_else(grepl("Regional", geo), "Regional", geo)) %>% 
  mutate(geo = str_to_title(geo)) %>% 
  filter(!is.na(geo)) %>% 
  tabyl(geo, survey) %>% 
  add_row(geo = "Total", English = 192, Spanish  = 255) %>% 
  pivot_longer(cols = English:Spanish, names_to = "survey", values_to = "value") %>% 
  group_by(survey) %>% 
  calc_shares(group = geo, denom = "Total", value = value)
```

Local news generally more popular than farther-out regions. Also note that one person wrote in Puerto Rico for the geographical question.

```{r echo = F}
response_geos %>%
  filter(!is.na(share)) %>% 
  filter(geo %in% c("Local", "State", "Regional", "National", "International")) %>% 
  mutate(geo = as.factor(geo),
         geo = fct_relevel(geo, "Local", "State", "Regional", "National", "International")) %>% 
  ggplot(aes(x = geo, y = share)) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), vjust = 1.2) +
  facet_grid(rows = vars(survey), switch = "y") +
  theme(axis.text.y = element_blank()) +
  labs(x = NULL, y = NULL, title = "Respondents by geographical interest")
```

```{r}
#Also hard coded denoms.

eng_topic <- tibble(topic = c(str_split(read_english$Q3, ", (?=[A-Z])", simplify = T)),
                  survey = "English")

spn_topic <- tibble(topic = c(str_split(read_spanish$Q3, ", (?=[A-Z])", simplify = T)),
                  survey = "Spanish")

response_topic <- bind_rows(eng_topic, spn_topic) %>%
  filter(topic != "") %>% 
  filter(!grepl("ratings", topic)) %>% #medical facilities = health
  add_row(topic = "Health", survey = "English") %>% 
  mutate(topic = if_else(grepl("arte", topic), "Music, arts, and culture", topic),
         topic = if_else(grepl("Educ", topic), "Education", topic),
         topic = if_else(grepl("Negocios", topic), "Local businesses", topic),
         topic = if_else(grepl("Eventos", topic), "Local events", topic),
         topic = if_else(grepl("Políticas", topic), "Politics", topic),
         topic = if_else(grepl("Salud", topic), "Health", topic),
         topic = if_else(grepl("Deportes", topic), "Sports", topic),
         topic = if_else(grepl("resources|Recursos", topic), "Community resources", topic),
         topic = if_else(grepl("Diversidad", topic), "Diversity and social justice", topic),
         topic = if_else(grepl("Tecno", topic), "Technology", topic),
         topic = if_else(grepl("Finanzas", topic), "Finance, wealth, and financial literacy", topic),
         topic = if_else(grepl("Oport", topic), "Opportunities for community engagement", topic),
         topic = if_else(grepl("Viajes", topic), "Travel and hospitality", topic),
         topic = if_else(grepl("cambio", topic), "Environmental issues & climate change", topic),
         topic = if_else(grepl("vivienda", topic), "Real estate and homeownership", topic),
         topic = if_else(topic == "Comida", "Food", topic)) %>% 
  mutate(topic = str_replace(topic, "&", "and"),
         topic = str_replace(topic, "Environmental", "Env."),
         topic = str_replace(topic, "Opportunities", "Opps."),
         topic = str_replace(topic, "Community", "Comm."),
         topic = str_replace(topic, "community", "comm.")) %>% 
  tabyl(topic, survey) %>% 
  filter(topic != "None") %>% 
  add_row(topic = "Total", English = 192, Spanish  = 255) %>% 
  pivot_longer(cols = English:Spanish, names_to = "survey", values_to = "value") %>% 
  group_by(survey) %>% 
  calc_shares(group = topic, denom = "Total", value = value)
```

We added Food in June so it's low now but will probably move up. Health, education, and local events continue to top this list.

```{r fig.height=6}
response_topic %>%
  filter(!is.na(share)) %>% 
  ggplot(aes(x = share, y = reorder(str_wrap(topic, 20), share))) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2) +
  facet_grid(cols = vars(survey)) +
  theme(axis.text.x = element_blank()) +
  labs(y = NULL, x = NULL, title = "Share of respondents by topics of interest")
```

```{r}
eng_special_topic <- tibble(topic = c(str_split(read_english$Q4, ", (?=[A-Z])", simplify = T)),
                    survey = "English") %>% 
  mutate(topic = str_remove(topic, "Topics related to "))
spn_special_topic <- tibble(topic = c(str_split(read_spanish$Q4, ", (?=[A-Z])", simplify = T)),
                    survey = "Spanish") %>% 
  mutate(topic = str_remove(topic, "Temas acerca de "))

response_special_topic <- bind_rows(eng_special_topic, spn_special_topic) %>%
  filter(topic != "") %>% 
  mutate(topic = str_to_sentence(topic)) %>% 
  mutate(topic = if_else(grepl("Familias", topic), "Families with children", topic),
         topic = if_else(grepl("Propietarios", topic), "Small business owners", topic),
         topic = if_else(grepl("edad", topic), "Seniors", topic),
         topic = if_else(grepl("Los", topic), "Teens", topic),
         topic = if_else(grepl("Jóvenes", topic), "Young adults", topic),
         topic = if_else(grepl("Participacion", topic), "Community engagement", topic)) %>%
  filter(!topic %in% c("None of these", "No", "Ninguno de estos")) %>% 
  tabyl(topic, survey) %>% 
  add_row(topic = "Total", English = 192, Spanish  = 255) %>% 
  pivot_longer(cols = English:Spanish, names_to = "survey", values_to = "value") %>% 
  group_by(survey) %>% 
  calc_shares(group = topic, denom = "Total", value = value)
```

Special topic areas being primarily focused on families makes sense with who we're surveying and how we're collecting responses.

```{r}
response_special_topic %>% 
  filter(!is.na(share)) %>% 
  mutate(topic = as.factor(topic),
         topic = fct_rev(topic)) %>% 
  ggplot(aes(x = share, y = reorder(topic, share))) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2) +
  facet_grid(cols = vars(survey)) +
  theme(axis.text.x = element_blank()) +
  labs(y = "Topics relevant to...", x = NULL, title = "Share of respondents by special topic area")
```

### Trust in news media

```{r}
trust <- tibble(national_news = as.factor(read_english$Q12),
                local_news = as.factor(read_english$Q13),
                social_media = as.factor(read_english$Q14),
                social_circle = as.factor(read_english$Q15),
                survey = as.factor("English")) %>% 
  bind_rows(tibble(national_news = as.factor(read_spanish$Q12),
                   local_news = as.factor(read_spanish$Q13),
                   social_media = as.factor(read_spanish$Q14),
                   social_circle = as.factor(read_spanish$Q15),
                   survey = as.factor("Spanish"))) %>% 
  pivot_longer(cols = national_news:social_circle, names_to = "level", values_to = "response") %>% 
  mutate(response = fct_collapse(response, `A lot` = c("A lot", "Mucho"),
                                 Some = c("Some", "Un poco"),
                                 `Not at all` = c("Not at all", "Para nada"))) %>% 
  group_by(survey, level, response) %>% 
  count() %>% 
  ungroup() %>%
  pivot_wider(id_cols = c("survey", "level"), names_from = "response", values_from = "n") %>% 
  select(-`NA`) %>% 
  mutate(`Not at all` = replace_na(`Not at all`, 0)) %>% 
  rowwise() %>% 
  mutate(total = sum(`A lot` + Some + `Not at all`, na.rm = T)) %>% 
  pivot_longer(cols = `A lot`:total, names_to = "response", values_to = "value") %>% 
  mutate(level = str_replace(level, "_", " "),
         level = str_to_sentence(level)) %>% 
  group_by(survey, level) %>% 
  camiller::calc_shares(group = response, denom = "total", value = value)
```

Higher levels of trust in social circles and national news for Spanish survey respondents makes sense based on which media they use and prefer, while for English survey respondents, there's a greater level of trust in local news.

```{r fig.width=7}
trust %>% 
  filter(!is.na(share)) %>% 
  mutate(response = fct_relevel(response, "A lot", "Some", "Not at all"),
         response = fct_rev(response),
         level = as.factor(level),
         level = fct_relevel(level, "National news", "Local news", "Social media", "Social circle"),
         level = fct_rev(level)) %>% 
  ggplot(aes(x = share, y = level, fill = response)) +
  geom_col(position = position_stack(.5), width = .8) +
  geom_text(data = . %>% filter(share >= .01), aes(label = scales::percent(share, accuracy = 1)), position = position_stack(.5)) +
  facet_grid(cols = vars(survey)) +
  scale_fill_manual(values = rev(opinion_pal)) +
  guides(fill = guide_legend(title = "Trust in source:", reverse = T)) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(x = NULL, y = NULL, title = "Share of respondents who trust news sources")
```

```{r}
labels <- tibble(code = c("Q1", "Q2", "Q3"), 
            question = c("I trust the sources of news I get about my community", "The local news covers issues that are important to me", "The local news reflects my beliefs and customs"))
                         
beliefs <- tibble(Q1 = read_english$Q16,
                Q2 = read_english$Q17,
                Q3 = read_english$Q18,
                survey = as.factor("English")) %>% 
  bind_rows(tibble(Q1 = read_spanish$Q16,
                   Q2 = read_spanish$Q17,
                   Q3 = read_spanish$Q18,
                   survey = as.factor("Spanish"))) %>% 
  pivot_longer(cols = Q1:Q3, names_to = "code", values_to = "response") %>% 
  mutate(response = if_else(response == "De acuerdo", "Agree", response),
         response = if_else(response == "En desacuerdo", "Disagree", response)) %>% 
  group_by(survey, code, response) %>% 
  count() %>% 
  ungroup() %>% 
  left_join(labels, by = "code") %>% 
  select(-code) %>% 
  pivot_wider(id_cols = c("survey", "question"), names_from = "response", values_from = "n") %>% 
  select(-`NA`) %>% 
  rowwise() %>% 
  mutate(Disagree = replace_na(Disagree, 0)) %>% 
  mutate(total = sum(Agree + Disagree + Neutral, na.rm = T)) %>% 
  pivot_longer(cols = Agree:total, names_to = "response", values_to = "value") %>% 
  group_by(survey, question) %>% 
  camiller::calc_shares(group = response, denom = "total", value = value) %>% 
  ungroup() %>% 
  filter(!is.na(share))
```

Spanish survey respondents are more likely to agree with these statements than English survey respondents, so I wonder if there's a cultural/political association here. I find it interesting that English survey respondents *trust* local news more but are less likely to agree that it reflects their beliefs.

```{r echo = F}
beliefs %>% 
  mutate(response = as.factor(response),
         response = fct_relevel(response, "Agree", "Neutral", "Disagree"),
         response = fct_rev(response)) %>% 
  ggplot(aes(x = share, y = str_wrap(question, 25), fill = response)) +
  geom_col(position = position_stack(), width = .8) +
  geom_text(data = . %>% filter(share >= .01), aes(label = scales::percent(share, accuracy = 1)), position = position_stack(.5)) +
  facet_grid(cols = vars(survey)) +
  scale_fill_manual(values = rev(opinion_pal)) +
  guides(fill = guide_legend(title = NULL, reverse = T)) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(x = NULL, y = NULL, title = str_wrap("Share of respondents agreeing with statements regarding trust in local news", 60))
```
