---
title: "News Topics & Areas of Interest"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, dpi = 170)
```

```{r libraries}
library(tidyverse)
library(cwi)
library(janitor)
library(camiller)
```

```{r paths}
source("../utils/plot_utils.R")
label_col <- c("#EDEEF2")
path <- "../survey_data/01032023/"
plot_path <- "../distro/"
read <- read_csv(paste(path, "clean.csv", sep = "")) %>% 
  rename(age = big_age_band)
```

## Geographic scope

More than half of respondents who speak Spanish at home are interested in international news. Local, state, and international levels are generally of the most interest.

```{r geos}
geo_age <- read %>%
  filter(latino == "Yes") %>% 
  filter(!is.na(age), !is.na(regions_of_interest)) %>%
  select(group = age, region = regions_of_interest) %>% 
  mutate(category = "age") %>% 
  separate_rows(region, sep = ";")

geo_latino <- read %>%
  filter(!is.na(latino), !is.na(regions_of_interest)) %>%
  select(group = latino, region = regions_of_interest) %>% 
  mutate(category = "latino") %>% 
  separate_rows(region, sep = ";")

geo_language <- read %>%
  filter(latino == "Yes") %>% 
  filter(!is.na(language), !is.na(regions_of_interest)) %>%
  select(group = language, region = regions_of_interest) %>% 
  mutate(category = "language") %>% 
  separate_rows(region, sep = ";")

geo_latinopob <- read %>%
  filter(latino == "Yes") %>% 
  filter(!is.na(latino_by_pob), !is.na(regions_of_interest)) %>%
  select(group = latino_by_pob, region = regions_of_interest) %>% 
  mutate(category = "latino_by_pob") %>% 
  separate_rows(region, sep = ";")

geo_total <- read %>%
  filter(!is.na(regions_of_interest)) %>%
  select(region = regions_of_interest) %>% 
  mutate(group = "total", category = "total") %>% 
  separate_rows(region, sep = ";")

denoms_geos <- read %>% 
  filter(!is.na(regions_of_interest)) %>% 
  mutate(category = "total", group = "total", region = "total") %>% 
  group_by(category, group, region) %>% 
  count()  %>% 
  bind_rows(read %>% 
              select(age, latino, language, latino_by_pob) %>% 
              pivot_longer(cols = everything(), names_to = "category", values_to = "group") %>% 
              group_by(category, group) %>% 
              count() %>% 
              filter(!is.na(group), group != "Opt out") %>% 
              mutate(region = "total"))

geos <- bind_rows(geo_age, geo_latino, geo_language, geo_latinopob, geo_total) %>% 
  select(category, group, everything()) %>%  
  filter(region != "None") %>% 
  mutate(region = if_else(region == "Estatal", "State", region),
         region = if_else(region == "Nacional", "National", region),
         region = if_else(grepl("Inter", region), "International", region),
         region = if_else(grepl("Regional", region), "Regional", region)) %>% 
  mutate(region = str_to_title(region)) %>% 
  group_by(category, group, region) %>% 
  count() %>% 
  filter(n >= 10, group != "Opt out") %>% 
  bind_rows(denoms_geos) %>% 
  ungroup() %>% 
  group_by(category, group) %>% 
  calc_shares(group = region, denom = "total", value = n) %>% 
  mutate(category = as.factor(category) %>%
           fct_relevel(., "total", "age", "language", "latino", "latino_by_pob"),
         group = as.factor(group),
         region = as.factor(region) %>%
           fct_relevel(., "Local", "State", "Regional", "National", "International"))

geos %>% 
  filter(!is.na(share), group != "Not Latino") %>% 
  ggplot(aes(x = share, y = fct_rev(group))) +
  geom_col(width = .8) +
  geom_text(data = . %>% filter(share >= .25), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, size = 3) +
  geom_text(data = . %>% filter(share < .25), aes(label = scales::percent(share, accuracy = 1)), hjust = -.2, size = 3, color = "black") +
  facet_grid(cols = vars(region), rows = vars(fct_rev(category)), space = "free", scales = "free_y") +
  theme(axis.text.x = element_blank()) +
  labs(title = "Regions of interest by category and group",
       subtitle = "Subgroups other than Latino y/n are Latinos. Regional = New England/NYC Metro", x = NULL, y = NULL)
```

## Topics

This list is really long, so breaking it out by category for four graphics.

```{r topics_table}
top_age <- read %>%
  filter(latino == "Yes") %>% 
  filter(!is.na(age), !is.na(topics_of_interest)) %>%
  select(group = age, topic = topics_of_interest) %>% 
  mutate(category = "age") %>% 
  separate_rows(topic, sep = ";")

top_gender <- read %>%
  filter(latino == "Yes") %>% 
  filter(!is.na(gender), !is.na(topics_of_interest)) %>%
  select(group = gender, topic = topics_of_interest) %>%
  mutate(category = "gender") %>%
  separate_rows(topic, sep = ";")

top_language <- read %>%
  filter(latino == "Yes") %>% 
  filter(!is.na(language), !is.na(topics_of_interest)) %>%
  select(group = language, topic = topics_of_interest) %>% 
  mutate(category = "language") %>% 
  separate_rows(topic, sep = ";")

top_poblatino <- read %>%
  filter(!is.na(latino_by_pob), !is.na(topics_of_interest)) %>%
  select(group = latino_by_pob, topic = topics_of_interest) %>% 
  mutate(category = "latino_by_pob") %>% 
  separate_rows(topic, sep = ";")

top_total <- read %>%
  filter(!is.na(topics_of_interest)) %>%
  select(topic = topics_of_interest) %>% 
  mutate(group = "total", category = "total") %>% 
  separate_rows(topic, sep = ";")

denoms_tops <- read %>% 
  filter(!is.na(topics_of_interest)) %>% 
  mutate(category = "total", group = "total", topic = "total") %>% 
  group_by(category, group, topic) %>% 
  count()  %>% 
  bind_rows(read %>% 
              filter(latino == "Yes") %>% 
              select(age, gender, language, latino_by_pob) %>% 
              pivot_longer(cols = everything(), names_to = "category", values_to = "group") %>% 
              group_by(category, group) %>% 
              count() %>% 
              filter(!is.na(group), group != "Opt out") %>% 
              mutate(topic = "total"))

topics <- bind_rows(top_age, top_gender, top_language, top_poblatino, top_total) %>% 
  select(category, group, everything()) %>%  
  filter(topic != "", !topic == "None") %>% 
  mutate(topic = if_else(grepl("arte|Music", topic), "Music, arts, and culture", topic),
         topic = if_else(grepl("Educ", topic), "Education", topic),
         topic = if_else(grepl("Negocios", topic), "Local businesses", topic),
         topic = if_else(grepl("Eventos", topic), "Local events", topic),
         topic = if_else(grepl("Políticas", topic), "Politics", topic),
         topic = if_else(grepl("Salud", topic), "Health", topic),
         topic = if_else(grepl("Deportes", topic), "Sports", topic),
         topic = if_else(grepl("resources|Recursos", topic), "Community resources", topic),
         topic = if_else(grepl("Diversidad", topic), "Diversity and social justice", topic),
         topic = if_else(grepl("Tecno", topic), "Technology", topic),
         topic = if_else(grepl("Finanzas", topic), "Finance, wealth, and financial literacy", topic),
         topic = if_else(grepl("Oport", topic), "Opportunities for community engagement", topic),
         topic = if_else(grepl("Viajes", topic), "Travel and hospitality", topic),
         topic = if_else(grepl("cambio", topic), "Environmental issues & climate change", topic),
         topic = if_else(grepl("vivienda", topic), "Real estate and homeownership", topic),
         topic = if_else(topic == "Comida", "Food", topic)) %>% 
  mutate(topic = str_replace(topic, "&", "and"),
         topic = str_replace(topic, "Environmental", "Env."),
         topic = str_replace(topic, "Opportunities", "Opps."),
         topic = str_replace(topic, "Community", "Comm."),
         topic = str_replace(topic, "community", "comm.")) %>% 
  mutate(topic = str_to_sentence(topic)) %>% 
  filter(group != "Opt out") %>% 
  group_by(category, group, topic) %>% 
  count() %>% 
  ungroup() %>% 
  filter(n >= 10) %>% 
  bind_rows(denoms_tops) %>% 
  group_by(group, category) %>% 
  calc_shares(group = topic, denom = "total", value = n)
```

Among all respondents, education and health still top the list. There are many, many write-ins here that I will share separately.

```{r top_total}
topics %>% 
  filter(!is.na(share), category == "total") %>% 
  ggplot(aes(x = share, y = reorder(topic, share))) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col) +
  scale_x_continuous(expand = expansion(mult = c(.01, .01))) +
  theme(axis.text.x = element_blank()) +
  labs(title = "Topics of interest (all respondents)", x = NULL, y = NULL)
```

I'm really surprised such a small share of young people selected environment/climate change. Music/arts/culture, education, and sports top the list for young people. Health, education, and music/arts/culture for the other two groups.

```{r top_age}
age_labels <- tibble(age = c("age00_29", "age30_49", "age50_99", "Total"),
                     label = c("Under 30", "30-49", "50 and over", "Total")) %>% 
  mutate(label = as.factor(label) %>% 
           fct_relevel(., "Total", "Under 30", "30-49", "50 and over"))

topics %>% 
  left_join(age_labels, by = c("group" = "age")) %>% 
  filter(!is.na(share), category == "age") %>% 
  ggplot(aes(x = share, y = reorder(topic, share), group = topic)) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), color = label_col, hjust = 1.2, size = 3.3) +
  #geom_point(aes(color = label, shape = label), size = 3, alpha = .75) +
  #scale_x_continuous(labels = scales::percent_format()) +
  scale_color_manual(values = c(cb_pal[1], cb_pal[4], cb_pal[8])) +
  facet_grid(cols = vars(label)) +
  #theme_bar(xgrid = T, ygrid = T) +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(title = "Topics of interest (by age)", x = NULL, y = NULL)
```

```{r top_gender}
topics %>% 
  filter(!is.na(share), category == "gender") %>% 
  ggplot(aes(x = share, y = reorder(topic, share), group = topic)) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), color = label_col, hjust = 1.2, size = 3.3) +
  #geom_point(aes(color = group, shape = group), size = 3, alpha = .75) +
  #scale_x_continuous(labels = scales::percent_format()) +
  #scale_color_manual(values = c(cb_pal[1], cb_pal[4], cb_pal[8])) +
  facet_grid(cols = vars(group)) +
  #theme_bar(xgrid = T, ygrid = T) +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(title = "Topics of interest (by gender)", x = NULL, y = NULL)
```

Looks like people who speak English at home also have an interest in local events, otherwise health, education, and music top the lists still, but Spanish-speakers also like to read about sports.

```{r top_language}
topics %>% 
  filter(!is.na(share), category == "language") %>% 
  ggplot(aes(x = share, y = reorder(topic, share))) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, size = 3.5) +
  facet_grid(cols = vars(group)) +
  theme(axis.text.x = element_blank()) +
  labs(title = "Topics of interest (by language spoken at home)", x = NULL, y = NULL)
```

Same general trends with sports ranking a bit higher among foreign-born Latinos.

```{r top_latinopob}
topics %>% 
  filter(!is.na(share), category == "latino_by_pob", group != "Not Latino") %>% 
  ggplot(aes(x = share, y = reorder(topic, share))) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col) +
  facet_grid(cols = vars(group)) +
  theme(axis.text.x = element_blank()) +
  labs(title = "Topics of interest (for Latinos by place of birth)", x = NULL, y = NULL)
```

## Special topics

No surprises in the ages 30-49 group wanting stories about families with kids/youth and respondents ages 50+ wanting stories about seniors.

```{r spec_tops}
spec_age <- read %>%
  filter(!is.na(age), !is.na(special_stories)) %>%
  select(group = age, story = special_stories) %>% 
  mutate(category = "age") %>% 
  separate_rows(story, sep = ";")

spec_gender <- read %>%
  filter(latino == "Yes") %>% 
  filter(!is.na(gender), !is.na(special_stories)) %>%
  select(group = gender, story = special_stories) %>% 
  mutate(category = "gender") %>% 
  separate_rows(story, sep = ";")

spec_language <- read %>%
  filter(!is.na(language), !is.na(special_stories)) %>%
  select(group = language, story = special_stories) %>% 
  mutate(category = "language") %>% 
  separate_rows(story, sep = ";")

spec_latinopob <- read %>%
  filter(!is.na(latino_by_pob), !is.na(special_stories)) %>%
  select(group = latino_by_pob, story = special_stories) %>% 
  mutate(category = "latino_by_pob") %>% 
  separate_rows(story, sep = ";")

spec_total <- read %>%
  filter(!is.na(special_stories)) %>%
  select(story = special_stories) %>% 
  mutate(group = "total", category = "total") %>% 
  separate_rows(story, sep = ";")

denoms_spec <- read %>% 
  filter(!is.na(special_stories)) %>% 
  mutate(category = "total", group = "total", story = "total") %>% 
  group_by(category, group, story) %>% 
  count()  %>% 
  bind_rows(read %>% 
  select(age, gender, language, latino_by_pob) %>% 
  pivot_longer(cols = everything(), names_to = "category", values_to = "group") %>% 
  group_by(category, group) %>% 
  count() %>% 
  filter(!is.na(group), group != "Opt out") %>% 
  mutate(story = "total"))

spec <- bind_rows(spec_age, spec_gender, spec_language, spec_latinopob, spec_total) %>% 
  select(category, group, everything()) %>% 
  mutate(story = str_remove(story, "Topics related to "),
         story = str_remove(story, "Temas acerca de ")) %>% 
  filter(story != "") %>% 
  mutate(story = str_to_sentence(story)) %>% 
  mutate(story = if_else(grepl("Familias", story), "Families with children", story),
         story = if_else(grepl("Propietarios", story), "Small business owners", story),
         story = if_else(grepl("edad", story), "Seniors", story),
         story = if_else(grepl("Los", story), "Teens", story),
         story = if_else(grepl("Jóvenes|adolescentes", story), "Young adults", story),
         story = if_else(grepl("Participacion", story), "Community engagement", story)) %>%
  filter(!story %in% c("None of these", "No", "Ninguno de estos")) %>% 
  group_by(category, group, story) %>% 
  count() %>% 
  filter(n >= 10, group != "Opt out") %>% 
  bind_rows(denoms_spec) %>% 
  ungroup() %>% 
  group_by(category, group) %>% 
  calc_shares(group = story, denom = "total", value = n) %>% 
  mutate(category = as.factor(category) %>%
           fct_relevel(., "total", "age", "language", "gender", "latino_by_pob"),
         group = as.factor(group))

spec %>% 
  filter(!is.na(share), group != "Not Latino") %>% 
  mutate(story = str_wrap(story, 12)) %>% 
  ggplot(aes(x = share, y = fct_rev(group))) +
  geom_col(width = .8) +
  geom_text(data = . %>% filter(share >= .3), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, size = 3.5) +
    geom_text(data = . %>% filter(share < .3), aes(label = scales::percent(share, accuracy = 1)), hjust = -.2, color = "black", size = 3.5) +
  facet_grid(cols = vars(story), rows = vars(fct_rev(category)), space = "free", scales = "free_y") +
  theme(axis.text.x = element_blank()) +
  labs(title = "Stories of interest by category and group", x = NULL, y = NULL)
```
