---
title: "News habits"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, dpi = 170)
```

```{r libraries}
library(tidyverse)
library(cwi)
library(janitor)
library(camiller)
source("../utils/plot_utils.R")
label_col <- c("#EDEEF2")
```

```{r paths}
path <- "../survey_data/01032023/"
plot_path <- "../distro/"
read <- read_csv(paste(path, "clean.csv", sep = "")) %>% 
  rename(age = big_age_band)

age_labels <- tibble(age = c("age00_29", "age30_49", "age50_99", "Total"),
                     label = c("Under 30", "30-49", "50 and over", "Total")) %>% 
  mutate(label = as.factor(label) %>% 
           fct_relevel(., "Total", "Under 30", "30-49", "50 and over"))
```

## Media used vs. Media preferred by total, age, and language at home

Overall totals not surprising. Strong preference for TV and social media. I think we can just look at "used."

```{r modes_used_preferred_total, fig.height=3.5}
prefread <- read %>% 
  mutate(formats_used = as.factor(formats_used),
         formats_used = fct_collapse(formats_used, TV = "TV", `Social media and friends` = c("Social media", "Social circles"),
                                     `Newspapers and apps` = c("Newspapers", "News apps/news websites"),
                                      `Radio or podcast` = c("Radio", "Podcast"),
                                     `Other sources` = c("Email/newsletter", "Text message"))) %>% 
  mutate(formats_preferred = as.factor(formats_preferred),
         formats_preferred = fct_collapse(formats_preferred, TV = "TV", `Social media and friends` = c("Social media", "Social circles"),
                                     `Newspapers and apps` = c("Newspapers", "News apps/news websites"),
                                     `Radio or podcast` = c("Radio", "Podcast"),
                                     `Other sources` = c("Email/newsletter", "Text message")))
modes_a <- prefread %>% 
  select(formats_used) %>% 
  filter(!is.na(formats_used)) %>% 
  group_by(formats_used) %>% 
  count() %>% 
  ungroup() %>%
  filter(n >= 3) %>% 
  group_by(formats_used) %>% 
  summarise(n = sum(n)) %>% 
  adorn_totals() %>% 
  rename(format = formats_used) %>% 
  mutate(mode = "Used")

modes_b <- prefread %>% 
  select(formats_preferred) %>% 
  filter(!is.na(formats_preferred)) %>% 
  group_by(formats_preferred) %>% 
  count() %>% 
  ungroup() %>%
  filter(n >= 3) %>%
  group_by(formats_preferred) %>% 
  summarise(n = sum(n)) %>% 
  adorn_totals() %>% 
  rename(format = formats_preferred) %>% 
  mutate(mode = "Preferred")

mode_bind <- bind_rows(modes_a, modes_b) %>% 
  group_by(mode) %>% 
  calc_shares(group = format, denom = "Total", value = n)

mode_bind %>% 
  filter(!is.na(share)) %>% 
  ggplot(aes(x = share, y = reorder(format, share)), group = format) +
  geom_path(color = "grey55", size = 1.5) +
  geom_point(aes(color = mode, shape = mode), size = 4) +
  theme_bar(ygrid = T) +
  ggrepel::geom_text_repel(aes(label = scales::percent(share, accuracy = 1), color = mode), vjust = -1.1, size = 3.4, family = "Barlow Semi Condensed", fontface = "bold") +
  ggrepel::geom_text_repel(data = . %>% filter(format == "TV"), aes(color = mode, label = mode), size = 3.4, vjust = -3, family = "Barlow Semi Condensed", fontface = "bold", min.segment.length = 1e5) +
  scale_y_discrete(expand = expansion(mult = c(0.02, 0.2))) +
  labs(title = "Ways respondents prefer/use to get news", x = NULL, y = NULL) +
  scale_color_manual(values = c(cb_pal[[1]], cb_pal[[4]])) +
  theme(axis.text.x = element_blank(),
        legend.position = "none")
```

I expected to see social media top the list for younger people. Social media just ekeing out ahead of TV for 30-49 year olds is interesting. We Millennials love a platform.

```{r modes_age}
agemode_denom <- prefread %>% 
  filter(latino == "Yes") %>% 
  select(formats_used, age) %>% 
  filter(!is.na(formats_used), !is.na(age)) %>% 
  group_by(age) %>% 
  count() %>% 
  mutate(format = "Total")
  
agemode1 <- prefread %>% 
  filter(latino == "Yes") %>% 
  select(formats_used, age) %>% 
  filter(!is.na(formats_used), !is.na(age)) %>% 
  group_by(formats_used, age) %>% 
  count() %>% 
  ungroup() %>% 
  filter(n >= 3) %>% 
  group_by(formats_used, age) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  rename(format = formats_used) %>% 
  bind_rows(agemode_denom) %>% 
  ungroup() %>% 
  group_by(age) %>% 
  calc_shares(group = format, denom = "Total", value = n)

agemode1 %>% 
  left_join(age_labels, by = "age") %>% 
  filter(format != "Total") %>% 
  ggplot(aes(x = share, y = reorder(format, share))) +
  geom_col() +
  geom_text(data = . %>% filter(share >= .15), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col) +
  geom_text(data = . %>% filter(share < .15), aes(label = scales::percent(share, accuracy = 1)), hjust = -.2) +
  facet_grid(cols = vars(label)) +
  labs(title = "How respondents get news, by age", subtitle = "Respondents could select multiple ways", x = NULL, y = NULL) +
  theme(axis.text.x = element_blank())
```

```{r mode_lang}
langmode_denom <- prefread %>% 
  filter(latino == "Yes") %>% 
  select(formats_used, language) %>% 
  filter(!is.na(formats_used), !is.na(language)) %>% 
  group_by(language) %>% 
  count() %>% 
  mutate(format = "Total")
  
langmode1 <- prefread %>% 
  filter(latino == "Yes") %>% 
  select(formats_used, language) %>% 
  filter(!is.na(formats_used), !is.na(language)) %>% 
  group_by(formats_used, language) %>% 
  count() %>% 
  ungroup() %>% 
  filter(n >= 3) %>% 
  group_by(formats_used, language) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  rename(format = formats_used) %>% 
  bind_rows(langmode_denom) %>% 
  ungroup() %>% 
  group_by(language) %>% 
  calc_shares(group = format, denom = "Total", value = n)

langmode1 %>% 
  filter(format != "Total") %>% 
  ggplot(aes(x = share, y = reorder(format, share))) +
  geom_col() +
  geom_text(data = . %>% filter(share >= .1), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col) +
  geom_text(data = . %>% filter(share < .1), aes(label = scales::percent(share, accuracy = 1)), hjust = -.2) +
  facet_grid(cols = vars(language)) +
  labs(title = "How respondents get news, by language spoken at home", subtitle = "Respondents could select multiple ways", x = NULL, y = NULL) +
  theme(axis.text.x = element_blank())
```

Huh, I expected more variation here, too. I guess TV and social media are really it.

```{r mode_gender}
gender_denom <- prefread %>% 
  select(gender, formats_used) %>% 
  filter(!is.na(formats_used), !is.na(gender)) %>% 
  group_by(gender) %>% 
  count() %>% 
  mutate(format = "Total")

gendermode1 <- prefread %>% 
  filter(latino == "Yes") %>% 
  select(formats_used, gender) %>% 
  filter(!is.na(formats_used), !is.na(gender)) %>% 
  group_by(formats_used, gender) %>% 
  count() %>% 
  ungroup() %>% 
  filter(n >= 3) %>% 
  group_by(formats_used, gender) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  rename(format = formats_used) %>% 
  bind_rows(gender_denom) %>% 
  ungroup() %>% 
  group_by(gender) %>% 
  calc_shares(group = format, denom = "Total", value = n)

gendermode1 %>% 
  filter(format != "Total", gender != "Transgender & NB") %>% 
  ggplot(aes(x = share, y = reorder(format, share))) +
  geom_col() +
  geom_text(data = . %>% filter(share >= .15), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col) +
  geom_text(data = . %>% filter(share < .15), aes(label = scales::percent(share, accuracy = 1)), hjust = -.2) +
  facet_grid(cols = vars(gender)) +
  labs(title = "How respondents get news, by gender", subtitle = "Respondents could select multiple ways", x = NULL, y = NULL) +
  theme(axis.text.x = element_blank())
```

```{r mode_pob_latino}
pobmodedenom <- prefread %>% 
  select(latino_by_pob, formats_used) %>% 
  filter(!is.na(formats_used), !is.na(latino_by_pob), latino_by_pob != "Not Latino") %>% 
  group_by(latino_by_pob) %>% 
  count() %>% 
  mutate(format = "Total")

pobmode1 <- prefread %>% 
  filter(latino == "Yes") %>% 
  select(formats_used, latino_by_pob) %>% 
  filter(!is.na(formats_used), !is.na(latino_by_pob), latino_by_pob != "Not Latino") %>% 
  group_by(formats_used, latino_by_pob) %>% 
  count() %>% 
  ungroup() %>% 
  filter(n >= 3) %>% 
  group_by(formats_used, latino_by_pob) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  rename(format = formats_used) %>% 
  bind_rows(pobmodedenom) %>% 
  ungroup() %>% 
  group_by(latino_by_pob) %>% 
  calc_shares(group = format, denom = "Total", value = n)

pobmode1 %>% 
  filter(format != "Total") %>% 
  ggplot(aes(x = share, y = reorder(format, share))) +
  geom_col() +
  geom_text(data = . %>% filter(share >= .15), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col) +
  geom_text(data = . %>% filter(share < .15), aes(label = scales::percent(share, accuracy = 1)), hjust = -.2) +
  facet_grid(cols = vars(latino_by_pob)) +
  labs(title = "How respondents get news, by age", subtitle = "Respondents could select multiple ways", x = NULL, y = NULL) +
  theme(axis.text.x = element_blank())
```

## Preferred language by age and ethnicity

```{r lang_pref_total, fig.height=3}
pref_all_denom <- read %>% 
  select(tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(format) %>% 
  count() %>% 
  mutate(language = "Total")

pref_all <- read %>% 
  select(tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(format, language) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(pref_all_denom) %>% 
  group_by(format) %>% 
  calc_shares(group = language, denom = "Total", value = n) %>% 
  mutate(format2 = str_replace_all(format, "_", " or "),
         format2 = str_to_sentence(format2),
         format2 = if_else(format2 == "Tv or video", "TV or video", format2))

pref_all %>% 
  filter(!language %in% c("I don't use this format", "Other", "Total")) %>% 
  ggplot(aes(x = share, y = format2, group = format2)) +
  geom_point(aes(color = language, shape = language), size = 4) +
  theme_bar(ygrid = T) +
  ggrepel::geom_text_repel(aes(label = scales::percent(share, accuracy = 1), color = language), vjust = -1.1, size = 3.4, family = "Barlow Semi Condensed", fontface = "bold") +
  ggrepel::geom_text_repel(data = . %>% filter(format == "tv_video"), aes(color = language, label = language), size = 3.4, vjust = -3, family = "Barlow Semi Condensed", fontface = "bold", min.segment.length = 1e5) +
  scale_y_discrete(expand = expansion(mult = c(0.03, 0.2))) +
  scale_color_manual(values = c(cb_pal[1], cb_pal[4], cb_pal[8])) +
  labs(title = "Preferred language by mode, all respondents", x = NULL, y = NULL) +
  theme(axis.text.x = element_blank(),
        legend.position = "none")
```

```{r lang_pref_age, fig.height=3}
pref_age_denom <- read %>% 
  filter(latino == "Yes") %>% 
  select(age, tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(age), !is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(age, format) %>% 
  count() %>% 
  mutate(language = "Total")

pref_age <- read %>% 
  filter(latino == "Yes") %>% 
  select(age, tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(age), !is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(age, format, language) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(pref_age_denom) %>% 
  group_by(age, format) %>% 
  calc_shares(group = language, denom = "Total", value = n) %>% 
  mutate(format2 = str_replace_all(format, "_", " or "),
         format2 = str_to_sentence(format2),
         format2 = if_else(format2 == "Tv or video", "TV or video", format2))

pref_age %>% 
  left_join(age_labels, by = "age") %>% 
  mutate(label = fct_rev(label)) %>% 
  filter(!language %in% c("I don't use this format", "Other", "Total")) %>% 
  ggplot(aes(x = share, y = label, group = label)) +
  geom_point(aes(color = language, shape = format2), size = 4, alpha = .75) +
  theme_bar(ygrid = T) +
  scale_y_discrete(expand = expansion(mult = c(0.03, 0.2))) +
  scale_x_continuous(labels = scales::percent_format()) +
  theme_bar(xgrid = T,ygrid = T) +
  scale_color_manual(values = c(cb_pal[1], cb_pal[4], cb_pal[8])) +
  guides(color = guide_legend(title = "Language"), shape = guide_legend(title = "Format")) +
  labs(title = "Preferred language by mode, by age", x = NULL, y = NULL) +
  theme(legend.position = "right")
```


```{r pref_gender, fig.height=3}
pref_gender_denom <- read %>% 
  filter(latino == "Yes") %>% 
  select(gender, tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(gender), !is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(gender, format) %>% 
  count() %>% 
  mutate(language = "Total")

pref_gender <- read %>% 
  select(gender, tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(gender), !is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(gender, format, language) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(pref_gender_denom) %>% 
  group_by(gender, format) %>% 
  calc_shares(group = language, denom = "Total", value = n) %>% 
  mutate(format2 = str_replace_all(format, "_", " or "),
         format2 = str_to_sentence(format2),
         format2 = if_else(format2 == "Tv or video", "TV or video", format2))

pref_gender %>% 
  filter(gender != "Transgender & NB", !language %in% c("I don't use this format", "Other", "Total")) %>% 
  ggplot(aes(x = share, y = gender, group = gender)) +
  geom_point(aes(color = language, shape = format2), size = 4, alpha = .75) +
  theme_bar(ygrid = T) +
  scale_y_discrete(expand = expansion(mult = c(0.03, 0.2))) +
  scale_x_continuous(labels = scales::percent_format()) +
  theme_bar(xgrid = T,ygrid = T) +
  scale_color_manual(values = c(cb_pal[1], cb_pal[4], cb_pal[8])) +
  guides(color = guide_legend(title = "Language"), shape = guide_legend(title = "Format")) +
  labs(title = "Preferred language by mode, by gender", x = NULL, y = NULL) +
  theme(legend.position = "right")
```

```{r pref_latino_pob, fig.height=3}
pref_latinopob_denom <- read %>% 
  select(latino_by_pob, tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(latino_by_pob), !is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(latino_by_pob, format) %>% 
  count() %>% 
  mutate(language = "Total")

pref_latinopob <- read %>% 
  select(latino_by_pob, tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(latino_by_pob), !is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(latino_by_pob, format, language) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(pref_latinopob_denom) %>% 
  group_by(latino_by_pob, format) %>% 
  calc_shares(group = language, denom = "Total", value = n) %>% 
  mutate(format2 = str_replace_all(format, "_", " or "),
         format2 = str_to_sentence(format2),
         format2 = if_else(format2 == "Tv or video", "TV or video", format2))

pref_latinopob %>% 
  filter(!language %in% c("I don't use this format", "Other", "Total"), latino_by_pob != "Not Latino") %>% 
  ggplot(aes(x = share, y = latino_by_pob, group = latino_by_pob)) +
  geom_point(aes(color = language, shape = format2), size = 4, alpha = .75) +
  theme_bar(ygrid = T) +
  scale_y_discrete(expand = expansion(mult = c(0.03, 0.2))) +
  scale_x_continuous(labels = scales::percent_format()) +
  theme_bar(xgrid = T,ygrid = T) +
  scale_color_manual(values = c(cb_pal[1], cb_pal[4], cb_pal[8])) +
  guides(color = guide_legend(title = "Language"), shape = guide_legend(title = "Format")) +
  labs(title = "Preferred language by mode, by place of birth", x = NULL, y = NULL) +
  theme(legend.position = "right")
```

```{r pref_langathome, fig.height=3}
pref_lang_denom <- read %>% 
  select(home_lang = language, tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(home_lang), !is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(home_lang, format) %>% 
  count() %>% 
  mutate(language = "Total")

pref_lang <- read %>% 
  select(home_lang = language, tv_video_language, radio_audio_language, print_language) %>% 
  pivot_longer(cols = ends_with("language"), names_to = "format", values_to = "language") %>% 
  filter(!is.na(home_lang), !is.na(format), !is.na(language)) %>% 
  mutate(format = str_remove(format, "_language")) %>% 
  group_by(home_lang, format, language) %>% 
  count() %>% 
  ungroup() %>% 
  bind_rows(pref_lang_denom) %>% 
  group_by(home_lang, format) %>% 
  calc_shares(group = language, denom = "Total", value = n) %>% 
  mutate(format2 = str_replace_all(format, "_", " or "),
         format2 = str_to_sentence(format2),
         format2 = if_else(format2 == "Tv or video", "TV or video", format2))

pref_lang %>% 
  filter(!language %in% c("I don't use this format", "Other", "Total")) %>% 
  ggplot(aes(x = share, y = home_lang, group = home_lang)) +
  geom_point(aes(color = language, shape = format2), size = 4, alpha = .75) +
  theme_bar(ygrid = T) +
  scale_y_discrete(expand = expansion(mult = c(0.03, 0.2))) +
  scale_x_continuous(labels = scales::percent_format()) +
  theme_bar(xgrid = T,ygrid = T) +
  scale_color_manual(values = c(cb_pal[1], cb_pal[4], cb_pal[8])) +
  guides(color = guide_legend(title = "Language"), shape = guide_legend(title = "Format")) +
  labs(title = "Preferred language by mode, by language spoken at home", x = NULL, y = NULL) +
  theme(legend.position = "right")
```


## News sources

Preferred sources is also an open text field. Mining for word clouds...

```{r mine_for_clouds}
age00_29 <- read %>% filter(latino == "Yes", age == "age00_29")
age30_49 <- read %>% filter(age == "age30_49")
age50_99 <- read %>% filter(age == "age50_99")

latino <- read %>% filter(latino == "Yes")

spn_at_home <- read %>% filter(latino == "Yes",language == "Spanish")
eng_at_home <- read %>% filter(latino == "Yes",language == "English")
both_at_home <- read %>% filter(latino == "Yes",language == "Both English and Spanish")

fblatino <- read %>% filter(latino == "Yes",latino_by_pob == "Foreign-born Latino")
uslatino <- read %>% filter(latino == "Yes",latino_by_pob == "US-born Latino")

men <- read %>% filter(latino == "Yes", gender == "Man")
women <- read %>% filter(latino == "Yes", gender == "Woman")

list_age00_29 <- str_split(age00_29$open_text_media, ",| y | and | or|\\/|  ", simplify = T)
list_age30_49 <- str_split(age30_49$open_text_media, ",| y | and | or|\\/|  ", simplify = T)
list_age50_99 <- str_split(age50_99$open_text_media, ",| y | and | or|\\/|  ", simplify = T)

list_latino <- str_split(latino$open_text_media, ",| y | and | or|\\/|  ", simplify = T)

list_spn_at_home <- str_split(spn_at_home$open_text_media, ",| y | and | or|\\/|  ", simplify = T)
list_eng_at_home <- str_split(eng_at_home$open_text_media, ",| y | and | or|\\/|  ", simplify = T)
list_both_at_home <- str_split(both_at_home$open_text_media, ",| y | and | or|\\/|  ", simplify = T)

list_fblatino <- str_split(fblatino$open_text_media, ",| y | and | or|\\/|  ", simplify = T)

list_uslatino <- str_split(uslatino$open_text_media, ",| y | and | or|\\/|  ", simplify = T)

list_total <- str_split(read$open_text_media, ",| y | and | or|\\/|  ", simplify = T)

list_men <- str_split(men$open_text_media, ",| y | and | or|\\/|  ", simplify = T)
list_women <- str_split(women$open_text_media, ",| y | and | or|\\/|  ", simplify = T)

clean_clouds <- function(x){
 x %>% 
    filter(!is.na(source), source != "") %>% 
    mutate(source = str_replace_all(source, "รณ", "o")) %>% 
    mutate(source = str_to_upper(source)) %>%
    mutate(source = str_trim(source, side = "both")) 
}

a <- tibble(source = c(list_age00_29)) %>% clean_clouds()
b <- tibble(source = c(list_age30_49)) %>% clean_clouds()
c <- tibble(source = c(list_age50_99)) %>% clean_clouds()
d <- tibble(source = c(list_latino)) %>% clean_clouds()
e <- tibble(source = c(list_spn_at_home)) %>% clean_clouds()
f <- tibble(source = c(list_eng_at_home)) %>% clean_clouds()
g <- tibble(source = c(list_both_at_home)) %>% clean_clouds()
h <- tibble(source = c(list_fblatino)) %>% clean_clouds()
i <- tibble(source = c(list_uslatino)) %>% clean_clouds()
j <- tibble(source = c(list_total)) %>% clean_clouds()
k <- tibble(source = c(list_men)) %>% clean_clouds()
l <- tibble(source = c(list_women)) %>% clean_clouds()

cloud_a <- a %>% group_by(source) %>% count()
cloud_b <- b %>% group_by(source) %>% count()
cloud_c <- c %>% group_by(source) %>% count()
cloud_d <- d %>% group_by(source) %>% count()
cloud_e <- e %>% group_by(source) %>% count()
cloud_f <- f %>% group_by(source) %>% count()
cloud_g <- g %>% group_by(source) %>% count()
cloud_h <- h %>% group_by(source) %>% count()
cloud_i <- i %>% group_by(source) %>% count()
cloud_j <- j %>% group_by(source) %>% count()
cloud_k <- k %>% group_by(source) %>% count()
cloud_l <- l %>% group_by(source) %>% count()
```

By age, young people put fewer answers in, older people put a lot more

```{r clouds_age}
library(ggwordcloud)

set.seed(13)

ggplot(cloud_a, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by Latinos under 30")

ggplot(cloud_b, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by Latinos 30-49")

ggplot(cloud_c, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by Latinos 50+")
```

Telemundo far and away the favored source for Latinos

```{r clouds_ethnicity}
ggplot(cloud_d, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5])+
  labs(title = "Sources preferred by Latinos")
```

Facebook stands out among Spanish speakers

```{r clouds_language, fig.width=6}
ggplot(cloud_e, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by Latinos who speak only Spanish at home")

ggplot(cloud_f, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by Latinos who speak only English at home")

ggplot(cloud_g, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by Latinos who speak English and Spanish at home")
```

Foreign-born Latinos use Facebook more (more access to news sources from abroad?)

```{r clouds_latinopob, fig.width=6}
ggplot(cloud_h, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by Foreign-born Latinos")

ggplot(cloud_i, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by US-born Latinos")
```

Total for good measure

```{r clouds_total, fig.width=6}
ggplot(cloud_j, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by all respondents")
```

Gender

```{r clouds_gender, fig.width=6}
ggplot(cloud_k, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by Latino men")

ggplot(cloud_l, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = gradient_pal[1], low = gradient_pal[5]) +
  labs(title = "Sources preferred by Latinas")
```
