---
title: "News habits"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r}
library(tidyverse)
library(cwi)
library(janitor)
library(camiller)
source("../utils/plot_utils.R")

#Cannot just re-run this! some denoms are hard-coded for non-response, and there's some text mining
```

```{r}
path <- "../survey_data/08302022/"
plot_path <- "../distro/"
```

```{r}
read_english <- read_csv(paste(path, "(English) RJ Latino Communities Reporting Lab Survey (Responses) - Form Responses 1.csv", sep = "")) %>% 
  clean_names()

read_spanish <- read_csv(paste(path, "(Spanish) RJ Latino Communities Reporting Lab Survey (Responses) - Form Responses 1.csv", sep = "")) %>% 
  clean_names()

qhead_eng <- tibble(question = paste("Q", 1:31, sep = ""),
                    label = colnames(read_english))
qhead_spn <- tibble(question = paste("Q", 1:31, sep = ""),
                    label = colnames(read_spanish))

colnames(read_english) <- qhead_eng$question
colnames(read_spanish) <- qhead_eng$question

read_english <- read_english %>% select(-Q29, -Q30) %>% remove_empty("rows")
read_spanish <- read_spanish %>% select(-Q29, -Q30) %>% remove_empty("rows")
```

Add PR festival data, hard code paths since it won't change, bind to primary surveys.

Just realized I deleted an entire section from the English PR Festival survey... I'll summarize what we have for the Spanish respondents, but the questions were those about what content they'd like to see.

```{r}
read_english_pr <- read_csv("../survey_data/08302022/(English - PR) RJ Latino Communities Reporting Lab Survey 2 2.csv") %>% 
  clean_names() %>% 
  mutate(`are_you_interested_in_news_at_the_following_geographical_levels_select_all_that_apply` = NA,
         `which_of_these_topics_interest_you_most_select_up_to_five` = NA,
         `do_any_of_these_special_stories_interest_you_select_all_that_apply` = NA,
         `are_there_any_specific_stories_you_would_like_to_see_more_of_in_local_news_for_example_investigative_articles_business_profiles_opinion_columns_cartoons_etc` = NA) %>% 
  select(timestamp, `are_you_interested_in_news_at_the_following_geographical_levels_select_all_that_apply`, `which_of_these_topics_interest_you_most_select_up_to_five`, `do_any_of_these_special_stories_interest_you_select_all_that_apply`, `are_there_any_specific_stories_you_would_like_to_see_more_of_in_local_news_for_example_investigative_articles_business_profiles_opinion_columns_cartoons_etc`, everything())

read_spanish_pr <- read_csv("../survey_data/08302022/(Spanish - PR) RJ Latino Communities Reporting Lab Survey (Responses) - Form Responses.csv") %>% 
  clean_names()

qhead_eng_pr <- tibble(question = paste("Q", 1:29, sep = ""),
                    label = colnames(read_english_pr))
qhead_spn_pr <- tibble(question = paste("Q", 1:29, sep = ""),
                    label = colnames(read_spanish_pr))

colnames(read_english_pr) <- qhead_spn_pr$question
colnames(read_spanish_pr) <- qhead_spn_pr$question

read_english_pr <- read_english_pr %>% remove_empty("rows")
read_spanish_pr <- read_spanish_pr %>% remove_empty("rows")

read_english <- read_english %>% bind_rows(read_english_pr) %>% rename(id = Q1)
read_spanish <- read_spanish %>% bind_rows(read_spanish_pr) %>% rename(id = Q1)
```

```{r}
age <- tibble(id = read_english$id,
              age = as.factor(read_english$Q22),
              survey = as.factor("English")) %>% 
  bind_rows(tibble(id = read_spanish$id,
                   age = as.factor(read_spanish$Q22),
                   survey = as.factor("Spanish"))) %>% 
  filter(!is.na(age)) %>% 
  mutate(age = if_else(age == "70 o mayor", "70 or older", as.character(age)),
         age = if_else(age == "Menor de 18", "Under 18", age)) %>% 
  filter(!age %in% c("Prefiero no decir", "Prefer not to say")) %>% 
  mutate(age = as.factor(age),
         age = fct_relevel(age, "Under 18", after = 0L)) %>% 
  mutate(age = fct_collapse(age, under_40 = c("Under 18", "18-29", "30-39"), over_40 = c("40-49", "50-59", "60-69", "70 or older")))
```

## Media used vs. Media preferred

I broke these into two charts by survey language and age so we can compare what medium they prefer to which they use more easily.

```{r}
response_mode <- tibble(id = read_english$id,
                        use_mode = as.factor(read_english$Q9),
                        pref_mode = as.factor(read_english$Q11),
                        survey = as.factor("English")) %>% 
  bind_rows(tibble(id = read_spanish$id,
                   use_mode = as.factor(read_spanish$Q9),
                   pref_mode = as.factor(read_spanish$Q11),
                   survey = as.factor("Spanish"))) %>% 
  filter(!is.na(pref_mode) & !is.na(use_mode)) %>% 
  mutate(clean_use = if_else(grepl("app|online|noticias", use_mode), "News apps", as.character(use_mode)),
         clean_use = if_else(use_mode %in% c("Medios sociales"), "Social media", clean_use),
         clean_use = if_else(grepl("Amistades|Friends|Familiares", clean_use), "Social circles", clean_use),
         clean_use = if_else(grepl("Correo", clean_use), "Email/newsletters", clean_use),
         clean_use = if_else(grepl("Periódicos", clean_use), "Newspapers", clean_use),
         clean_use = if_else(clean_use == "Textos", "Text message", clean_use)) %>% 
  mutate(clean_pref = if_else(grepl("app|online|noticias|Same", pref_mode), "News apps", as.character(pref_mode)),
         clean_pref = if_else(pref_mode %in% c("Medios sociales"), "Social media", clean_pref),
         clean_pref = if_else(grepl("Amistades|Friends|Familiares", clean_pref), "Social circles", clean_pref),
         clean_pref = if_else(grepl("Correo|Email", clean_pref), "Email/newsletters", clean_pref),
         clean_pref = if_else(grepl("Periódicos", clean_pref), "Newspapers", clean_pref),
         clean_pref = if_else(clean_pref == "Textos", "Text message", clean_pref),
         clean_pref = if_else(clean_pref == "Celular", "Text message", clean_pref)) %>% 
  left_join(age, by = c("survey", "id")) %>% 
  select(survey, clean_use, clean_pref, age)

mode_to_plot <- response_mode %>%
  select(survey, mode = clean_use, age) %>%
  filter(!is.na(age)) %>% 
  group_by(mode, age, survey) %>% 
  count() %>% 
  ungroup() %>%
  group_by(survey, age) %>% 
  mutate(total = sum(n)) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(share = n / total,
         type = "Use") %>% 
  bind_rows(response_mode %>%
              select(survey, mode = clean_pref, age) %>%
              filter(!is.na(age)) %>% 
              group_by(mode, age, survey) %>% 
              count() %>% 
              ungroup() %>%
              group_by(survey, age) %>% 
              mutate(total = sum(n)) %>% 
              ungroup() %>% 
              rowwise() %>% 
              mutate(share = n / total,
                     type = "Prefer")) %>% 
  ungroup()
```

For English language respondents under 40, social media is by far the most popular way people use to get news and prefer to get news. The over-40 crowd prefers TV. There's a bigger preference than use for news apps (I wonder if people know they exist) and newspapers (cost? access?). Again, newsletters might be something to promote.

```{r}
# add_rows <- tibble(mode = c(rep("Social circles", 2), rep("Internet", 3)),
#                    age = c("under_40", "over_40", "under_40", "over_40", "over_40"),
#                    survey = c(rep("English", 5)),
#                    n = c(rep(0, 5)),
#                    total = c(76, 110, 76, 110, 110),
#                    share = c(rep(0, 5)),
#                    type = c(rep("Prefer", 4), "Use")) %>% 
#   mutate(age = as.factor(age),
#          survey = as.factor(survey))

mode_to_plot %>% 
  filter(survey == "English", ,
         n >= 5) %>% 
  #bind_rows(add_rows) %>% 
  ggplot(aes(x = share, y = reorder(mode, share), group = type)) +
  geom_col(aes(fill = type), position = position_dodge(.9)) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), hjust = 1, color = "black") +
  facet_grid(cols = vars(age), space = "free") +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
      scale_fill_manual(values = unname(qual_pal[c("violet", "cyan")])) +
  labs(title = "News source preferences/use by age, English language respondents",
       x = NULL, y = NULL)
```

I'm a bit surprised to see TV and social media pretty comparable for Spanish language respondents under 40. Fully half of respondents over 40 prefer TV (accessible? covering more topics they're interested in?). While not as popular as social media, again, news apps and newsletters might be something to promote.

```{r}
# add_rows2 <- tibble(mode = c(rep("Social circles", 1), rep("Internet", 3)),
#                    age = c("over_40", "under_40", "under_40", "over_40"),
#                    survey = c(rep("Spanish", 4)),
#                    n = c(rep(0, 4)),
#                    total = c(157, 93, 93, 157),
#                    share = c(rep(0, 4)),
#                    type = c("Prefer", "Use", "Prefer", "Use")) %>% 
#   mutate(age = as.factor(age),
#          survey = as.factor(survey))

mode_to_plot %>% 
  filter(survey == "Spanish",
         n >= 5) %>% 
  #bind_rows(add_rows2) %>% 
  ggplot(aes(x = share, y = reorder(mode, share), group = type)) +
  geom_col(aes(fill = type), position = position_dodge(.9)) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), hjust = 1, color = "black") +
  facet_grid(cols = vars(age), space = "free") +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
    scale_fill_manual(values = unname(qual_pal[c("violet", "cyan")])) +
  labs(title = "News source preferences/use by age, Spanish language respondents",
       x = NULL, y = NULL)
```

## Preferred language

```{r}
pref_lang <- tibble(tv_video = read_english$Q6,
                    radio_audio = read_english$Q7,
                    print = read_english$Q8,
                    survey = as.factor("English")) %>% 
  bind_rows(tibble(tv_video = read_spanish$Q6,
                   radio_audio = read_spanish$Q7,
                   print = read_spanish$Q8,
                   survey = as.factor("Spanish"))) %>% 
  mutate(tv_video = if_else(grepl("Inglés", tv_video), "English", tv_video),
         tv_video = if_else(grepl("Español", tv_video), "Spanish", tv_video),
         tv_video = if_else(grepl("Ambos", tv_video), "Both English and Spanish", tv_video),
         tv_video = if_else(grepl("Otro", tv_video), "Other", tv_video)) %>% 
  mutate(radio_audio = if_else(grepl("Inglés", radio_audio), "English", radio_audio),
         radio_audio = if_else(grepl("Español", radio_audio), "Spanish", radio_audio),
         radio_audio = if_else(grepl("Ambos", radio_audio), "Both English and Spanish", radio_audio),
         radio_audio = if_else(grepl("Otro", radio_audio), "Other", radio_audio)) %>% 
  mutate(print = if_else(grepl("Inglés", print), "English", print),
         print = if_else(grepl("Español", print), "Spanish", print),
         print = if_else(grepl("Ambos", print), "Both English and Spanish", print),
         print = if_else(grepl("Otro", print), "Other", print))
pref_lang_to_plot <- pref_lang %>%
  select(survey, language = tv_video) %>%
  filter(!is.na(language), !language %in% c("I don't use this format", "No uso este formato")) %>% 
  tabyl(language, survey) %>% 
  adorn_totals("row") %>% 
  mutate(type = "TV/Video") %>% 
  bind_rows(pref_lang %>% 
              select(survey, language = radio_audio) %>% 
              filter(!is.na(language), !language %in% c("I don't use this format", "No uso este formato")) %>%  
              tabyl(language, survey) %>% 
              adorn_totals("row") %>% 
              mutate(type = "Radio/Audio")) %>% 
  bind_rows(pref_lang %>% 
              select(survey, language = print) %>% 
              filter(!is.na(language), !language %in% c("I don't use this format", "No uso este formato")) %>%  
              tabyl(language, survey) %>% 
              adorn_totals("row") %>% 
              mutate(type = "Print")) %>% 
  pivot_longer(cols = English:Spanish, names_to = "survey", values_to = "value") %>% 
  group_by(survey, type) %>% 
  calc_shares(group = language, denom = "Total", value = value)
```

With language, again a strong preference towards the survey language and "both." In future focus groups if we can ask people who prefer both why they do, that would be helpful.

```{r}
pref_lang_to_plot %>% 
  filter(!is.na(share), language != "Other") %>% 
  ggplot(aes(x = language, y = share)) +
  geom_col(aes(fill = language), position = position_dodge(.9), width = .8) +
  geom_text(data = . %>% filter(share > 0.1), aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), vjust = 1.2) +
  geom_text(data = . %>% filter(share <= 0.1), aes(label = scales::percent(share, accuracy = 1)), position = position_dodge(.9), vjust = -.2, color = "grey20") +
  guides(fill = guide_legend(title = NULL)) +
  facet_grid(rows = vars(survey), cols = vars(type), scales = "free_y", switch = "y") +
 scale_fill_manual(values = unname(qual_pal[c("violet", "cyan", "pink", "teal", "indigo")])) +
  theme(legend.position = "bottom",
        axis.text.x = element_blank(),
        axis.text.y = element_blank()) +
  labs(x = NULL, y = "Survey language", title = "Share of respondents by preferred langauge by mode")
```

## News sources

Preferred sources is also an open text field. Mining for a word cloud...

```{r}
eng_list <- str_split(read_english$Q10, ",| y | and | or|\\/|  ", simplify = T)
spn_list <- str_split(read_spanish$Q10, ",| y | and | or|\\/|  ", simplify = T)

add_back <- tibble(source = c("FACEBOOK", "GOOGLE", "HARTFORD COURANT", "TELEMUNDO", "WFSB", "TELEFE INTERNATIONAL", "RECORD-JOURNAL", "FACEBOOK", "HARTFORD COURANT", "CT POST", "WTNH", "TELEMUNDO", "CNN", "INSTAGRAM", "INSTAGRAM"))
                              
                              
x <- tibble(source = c(spn_list, eng_list)) %>% 
  filter(!is.na(source), source != "") %>% 
  mutate(source = str_to_upper(source)) %>%
  mutate(source = str_trim(source, side = "both")) %>% 
  mutate(source = str_remove(source,  c(" IF AVAILABLE| PRINT EDITION"))) %>% 
  # filter(!source %in% c("N", "A", "FACEBOOK GOOGLE", "HARTFORD COURANT TELEMUNDO WFSB 3 TELEFE INTERNATIONAL", "RECORD JOURNAL FACEBOOK", "HARTFORD COURANT CT POST WTNH", "TODO", "TODOS", "UN POCO DE TODO", "USUALLY TELEMUNDO", "NONE", "CNN E INSTAGRAM", "IG")) %>% #will add these back properly below
  mutate(source = if_else(grepl("RECORD|RJ|R-J", source), "RECORD-JOURNAL", source),
         source = if_else(grepl("NBC|CHANNEL 30", source), "NBC", source),
         source = if_else(grepl("FOX", source), "FOX NEWS", source),
         source = if_else(grepl("CHANNEL 8", source), "WTNH", source),
         source = if_else(grepl("CHANNEL 3|CHANEL 3|WFSB", source), "WFSB", source),
         source = if_else(grepl("BREAK", source), "NEWSBREAK", source),
         source = if_else(grepl("LOCAL", source), "LOCAL STATIONS", source),
         source = if_else(grepl("HEARALD", source), "NEW BRITAIN HERALD", source),
         source = if_else(grepl("WAPO", source), "WASHINGTON POST", source),
         source = if_else(grepl("UNIV", source), "UNIVISION", source)) %>% 
  mutate(source = str_trim(source, side = "both"))

cloud <- x %>% group_by(source) %>% count()
```

```{r}
library(ggwordcloud)

set.seed(13)

ggplot(cloud, aes(label = source, size = n+3, color = n)) +
  geom_text_wordcloud_area(family = "Barlow Semi Condensed", eccentricity = .6) +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  scale_color_gradient(high = qual_pal[1], low = qual_pal[7])
```

## Geographic scope

```{r}
#Denoms are hard-coded so we get share of respondents, not share of responses

eng_geo <- tibble(geo = c(str_split(read_english$Q2, ", ", simplify = T)),
                  survey = "English")
spn_geo <- tibble(geo = c(str_split(read_spanish$Q2, ", ", simplify = T)),
                  survey = "Spanish")

response_geos <- bind_rows(eng_geo, spn_geo) %>% 
  filter(!geo %in% c("", "No", "None", "Yo'u're too biased.  way too liberal.", "PUERTO RICO")) %>% 
  mutate(geo = if_else(geo == "Estatal", "State", geo),
         geo = if_else(geo == "Nacional", "National", geo),
         geo = if_else(grepl("Inter", geo), "International", geo),
         geo = if_else(grepl("Regional", geo), "Regional", geo)) %>% 
  mutate(geo = str_to_title(geo)) %>% 
  filter(!is.na(geo)) %>% 
  tabyl(geo, survey) %>% 
  add_row(geo = "Total", English = 443, Spanish  = 550) %>% 
  pivot_longer(cols = English:Spanish, names_to = "survey", values_to = "value") %>% 
  group_by(survey) %>% 
  calc_shares(group = geo, denom = "Total", value = value)
```

Local news generally more popular than farther-out regions. Also note that one person wrote in Puerto Rico for the geographical question.

```{r echo = F}
response_geos %>%
  filter(!is.na(share)) %>% 
  filter(geo %in% c("Local", "State", "Regional", "National", "International")) %>% 
  mutate(geo = as.factor(geo),
         geo = fct_relevel(geo, "Local", "State", "Regional", "National", "International")) %>% 
  ggplot(aes(x = geo, y = share)) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), vjust = 1.2) +
  facet_grid(rows = vars(survey), switch = "y") +
  theme(axis.text.y = element_blank()) +
  labs(x = NULL, y = NULL, title = "Respondents by geographical interest")
```

## Topics

```{r}
#Also hard coded denoms.

eng_topics_under40 <- read_english %>% 
  select(id, Q3) %>% 
  left_join(age, by = "id") %>% 
  filter(age == "under_40") %>% 
  select(Q3)

eng_topics_over40 <- read_english %>% 
  select(id, Q3) %>% 
  left_join(age, by = "id") %>% 
  filter(age == "over_40") %>% 
  select(Q3)

spn_topics_under40 <- read_spanish %>% 
  select(id, Q3) %>% 
  left_join(age, by = "id") %>% 
  filter(age == "under_40") %>% 
  select(Q3)

spn_topics_over40 <- read_spanish %>% 
  select(id, Q3) %>% 
  left_join(age, by = "id") %>% 
  filter(age == "over_40") %>% 
  select(Q3)

eng_topic_list1 <- tibble(topic = c(str_split(eng_topics_under40$Q3, ", (?=[A-Z])", simplify = T)),
                         age = "under_40",
                         survey = "English")
eng_topic_list2 <- tibble(topic = c(str_split(eng_topics_over40$Q3, ", (?=[A-Z])", simplify = T)),
                         age = "over_40",
                         survey = "English")
spn_topic_list1 <- tibble(topic = c(str_split(spn_topics_under40$Q3, ", (?=[A-Z])", simplify = T)),
                         age = "under_40",
                         survey = "Spanish")
spn_topic_list2 <- tibble(topic = c(str_split(spn_topics_over40$Q3, ", (?=[A-Z])", simplify = T)),
                         age = "over_40",
                         survey = "Spanish")

denoms <- tibble(survey = c(rep("English", 2), rep("Spanish", 2)),
                 age = c("under_40", "over_40", "under_40", "over_40"),
                 total = c(169, 265, 190, 351))

response_topic <- bind_rows(eng_topic_list1, eng_topic_list2, spn_topic_list1, spn_topic_list2) %>%
  filter(!is.na(age)) %>% 
  filter(topic != "") %>% 
  filter(!topic == "None") %>% 
  filter(!grepl("ratings", topic)) %>% #medical facilities = health
  add_row(topic = "Health", survey = "English") %>% 
  mutate(topic = if_else(grepl("arte", topic), "Music, arts, and culture", topic),
         topic = if_else(grepl("Educ", topic), "Education", topic),
         topic = if_else(grepl("Negocios", topic), "Local businesses", topic),
         topic = if_else(grepl("Eventos", topic), "Local events", topic),
         topic = if_else(grepl("Políticas", topic), "Politics", topic),
         topic = if_else(grepl("Salud", topic), "Health", topic),
         topic = if_else(grepl("Deportes", topic), "Sports", topic),
         topic = if_else(grepl("resources|Recursos", topic), "Community resources", topic),
         topic = if_else(grepl("Diversidad", topic), "Diversity and social justice", topic),
         topic = if_else(grepl("Tecno", topic), "Technology", topic),
         topic = if_else(grepl("Finanzas", topic), "Finance, wealth, and financial literacy", topic),
         topic = if_else(grepl("Oport", topic), "Opportunities for community engagement", topic),
         topic = if_else(grepl("Viajes", topic), "Travel and hospitality", topic),
         topic = if_else(grepl("cambio", topic), "Environmental issues & climate change", topic),
         topic = if_else(grepl("vivienda", topic), "Real estate and homeownership", topic),
         topic = if_else(topic == "Comida", "Food", topic)) %>% 
  mutate(topic = str_replace(topic, "&", "and"),
         topic = str_replace(topic, "Environmental", "Env."),
         topic = str_replace(topic, "Opportunities", "Opps."),
         topic = str_replace(topic, "Community", "Comm."),
         topic = str_replace(topic, "community", "comm.")) %>% 
  group_by(survey, age, topic) %>% 
  count() %>% 
  ungroup() %>% 
  left_join(denoms, by = c("survey", "age")) %>% 
  rowwise() %>% 
  mutate(share = n / total) %>% 
  ungroup()
```

Over and under 40 for the English language survey have the same top 5 or so topics of interest with Education, Music/Arts/Culture, and Health topping the lists.

```{r fig.height=6}
response_topic %>% 
  filter(survey == "English", n >= 10) %>% 
  ggplot(aes(x = share, y = reorder(topic, share))) +
  geom_col() +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.1) +
  facet_grid(cols = vars(age)) +
  labs(title = "Topics of interest by age, English survey respondents", x = NULL, y = NULL) +
  theme(axis.text.x = element_blank())
```

Health and Education top the list for Spanish survey respondents in both age groups. For younger people, the next three are Sports, Politics, and Music/Arts/Culture. For older people it's Sports, Music/Arts/Culture, and Local Events.

```{r fig.height=6}
response_topic %>% 
  filter(survey == "Spanish", n >= 10) %>% 
  ggplot(aes(x = share, y = reorder(topic, share))) +
  geom_col() +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.1) +
  facet_grid(cols = vars(age)) +
  labs(title = "Topics of interest by age, Spanish survey respondents", x = NULL, y = NULL) +
  theme(axis.text.x = element_blank())
```

## Special topics

```{r}
eng_special_topic <- tibble(topic = c(str_split(read_english$Q4, ", (?=[A-Z])", simplify = T)),
                    survey = "English") %>% 
  mutate(topic = str_remove(topic, "Topics related to "))
spn_special_topic <- tibble(topic = c(str_split(read_spanish$Q4, ", (?=[A-Z])", simplify = T)),
                    survey = "Spanish") %>% 
  mutate(topic = str_remove(topic, "Temas acerca de "))

response_special_topic <- bind_rows(eng_special_topic, spn_special_topic) %>%
  filter(topic != "") %>% 
  mutate(topic = str_to_sentence(topic)) %>% 
  mutate(topic = if_else(grepl("Familias", topic), "Families with children", topic),
         topic = if_else(grepl("Propietarios", topic), "Small business owners", topic),
         topic = if_else(grepl("edad", topic), "Seniors", topic),
         topic = if_else(grepl("Los", topic), "Teens", topic),
         topic = if_else(grepl("Jóvenes|adolescentes", topic), "Young adults", topic),
         topic = if_else(grepl("Participacion", topic), "Community engagement", topic)) %>%
  filter(!topic %in% c("None of these", "No", "Ninguno de estos")) %>% 
  filter(!grepl("subscribe", topic)) %>% 
  tabyl(topic, survey) %>% 
  add_row(topic = "Total", English = 443, Spanish  = 550) %>% 
  pivot_longer(cols = English:Spanish, names_to = "survey", values_to = "value") %>% 
  group_by(survey) %>% 
  calc_shares(group = topic, denom = "Total", value = value)
```

Special topic areas being primarily focused on families makes sense with who we're surveying and how we're collecting responses.

```{r}
response_special_topic %>% 
  filter(value > 1) %>% 
  filter(!is.na(share)) %>% 
  mutate(topic = as.factor(topic),
         topic = fct_rev(topic)) %>% 
  ggplot(aes(x = share, y = reorder(topic, share))) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2) +
  facet_grid(cols = vars(survey)) +
  theme(axis.text.x = element_blank()) +
  labs(y = "Topics relevant to...", x = NULL, title = "Share of respondents by special topic area")
```

