---
title: "Trust in news media"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, dpi = 170, fig.height = 3)
```

```{r libraries}
library(tidyverse)
library(cwi)
library(janitor)
library(camiller)
source("../utils/plot_utils.R")
label_col <- c("#EDEEF2")
```

```{r paths}
path <- "../survey_data/01032023/"
plot_path <- "../distro/"
read <- read_csv(paste(path, "clean.csv", sep = "")) %>% 
  rename(age = big_age_band)
```

## Trustworthiness by source by group

```{r make_trust}
trust_all <- read %>% select(trust_national_news, trust_local_news, trust_social_media_news, trust_news_from_social_circle) %>% 
  mutate(category = "total", group = "total") %>% 
  pivot_longer(cols = starts_with("trust"), names_to = "level", names_prefix = "trust_", values_to = "response")

trust <- read %>% 
  select(age, gender, language, latino_by_pob, trust_national_news, trust_local_news, trust_social_media_news, trust_news_from_social_circle) %>% 
  pivot_longer(cols = starts_with("trust"), names_to = "level", names_prefix = "trust_", values_to = "response") %>%
  pivot_longer(cols = age:latino_by_pob, names_to = "category", values_to = "group") %>% 
  bind_rows(trust_all) %>% 
  mutate(level = str_replace_all(level, "_", " "),
         level = str_to_sentence(level)) %>% 
  mutate(response = if_else(response == "Not at all", response, "Some or a lot"))
```

```{r trust_total}
trust_total <- trust %>% 
  filter(category == "total", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, level, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "level"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(`Some or a lot`, `Not at all`)) %>% 
  pivot_longer(cols = c("Some or a lot", "Not at all", "Total"), names_to = "response", values_to = "n") %>%
  mutate(response = as.factor(response) %>% fct_relevel(., "Some or a lot", "Not at all")) %>% 
  group_by(category, group, level) %>% 
  calc_shares(group = response, denom = "Total", value = n)

trust_total %>% 
  filter(response == "Some or a lot") %>% 
  ggplot(aes(x = share, y = reorder(level, share))) +
  geom_col(width = .8) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col) +
  theme(legend.position = "none",
        axis.text.x = element_blank()) +
  labs(title = "Some or a lot of trust in different sources of news, all respondents", x = NULL, y = NULL)
```

Local news tops the trustworthiness list among all age groups. Older adults are more skeptical of social media/social circles. I wonder if that's related to whether or not they even use those sources.

```{r age_trust, fig.height=3.5}
age_labels <- tibble(age = c("age00_29", "age30_49", "age50_99", "Total"),
                     label = c("Under 30", "30-49", "50 and over", "Total")) %>% 
  mutate(label = as.factor(label) %>% 
           fct_relevel(., "Total", "Under 30", "30-49", "50 and over"))

age_trust <- trust %>% 
  filter(category == "age", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, level, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "level"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(`Some or a lot`, `Not at all`)) %>% 
  pivot_longer(cols = c("Some or a lot", "Not at all", "Total"), names_to = "response", values_to = "n") %>%
  mutate(response = as.factor(response) %>% fct_relevel(., "Some or a lot", "Not at all")) %>% 
  group_by(category, group, level) %>% 
  calc_shares(group = response, denom = "Total", value = n)

age_trust %>% 
  left_join(age_labels, by = c("group" = "age")) %>% 
  mutate(label = fct_rev(label)) %>% 
  filter(response == "Some or a lot") %>% 
  ggplot(aes(x = share, y = reorder(level, share), group = label)) +
  geom_col(aes(fill = label), width = .8, position = position_dodge(.9)) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = "black", position = position_dodge(.9)) +
  geom_text(data = . %>% filter(label == "30-49"), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, position = position_dodge(.9)) +
  theme(legend.position = "bottom", axis.text.x = element_blank()) +
  guides(fill = guide_legend(title = NULL, rev = T)) +
  scale_fill_manual(values = rev(c(cb_pal[1], cb_pal[4], cb_pal[8]))) +
  labs(title = "Some or a lot of trust in different sources of news, by age", x = NULL, y = NULL)
```

Latinos trust social media news at more than twice the rate of non-Latinos. Again local news tops the list, but Latinos also trust national news sources (Telemundo, etc.) at a higher rate than non-Latinos. Again, like social media among older people, I wonder if it's that non-Latinos tend to prefer local news.

```{r gender_trust}
gender_trust <- trust %>% 
  filter(category == "gender", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, level, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "level"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(`Some or a lot`, `Not at all`)) %>% 
  pivot_longer(cols = c("Some or a lot", "Not at all", "Total"), names_to = "response", values_to = "n") %>%
  mutate(response = as.factor(response) %>% fct_relevel(., "Some or a lot", "Not at all")) %>% 
  group_by(category, group, level) %>% 
  calc_shares(group = response, denom = "Total", value = n)

gender_trust %>% 
  filter(response == "Some or a lot", group != "Transgender & NB") %>% 
  ggplot(aes(x = share, y = reorder(level, share), group = group)) +
  geom_col(aes(fill = group), width = .8, position = position_dodge(.9)) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, position = position_dodge(.9)) +
  theme(legend.position = "bottom", axis.text.x = element_blank()) +
  guides(fill = guide_legend(title = NULL, rev = T)) +
  scale_fill_manual(values = c(cb_pal[1], cb_pal[4])) +
  labs(title = "Some or a lot of trust in different sources of news, by gender", x = NULL, y = NULL)
```

Similar trend in people who speak Spanish or both languages at home-- greater trust in national news sources. People who speak English at home generally distrust social media more.

```{r lang_trust, fig.height=3.5}
lang_trust <- trust %>% 
  filter(category == "language", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, level, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "level"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(`Some or a lot`, `Not at all`)) %>% 
  pivot_longer(cols = c("Some or a lot", "Not at all", "Total"), names_to = "response", values_to = "n") %>%
  mutate(response = as.factor(response) %>% fct_relevel(., "Some or a lot", "Not at all")) %>% 
  group_by(category, group, level) %>% 
  calc_shares(group = response, denom = "Total", value = n)

lang_trust %>% 
  filter(response == "Some or a lot") %>% 
  mutate(group = as.factor(group),
        group = fct_rev(group)) %>% 
  ggplot(aes(x = share, y = reorder(level, share), group = group)) +
  geom_col(aes(fill = group), width = .8, position = position_dodge(.9)) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = "black", position = position_dodge(.9)) +
  geom_text(data = . %>% filter(group == "English"), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, position = position_dodge(.9)) +
  theme(legend.position = "bottom", axis.text.x = element_blank()) +
  guides(fill = guide_legend(title = NULL, rev = T)) +
  scale_fill_manual(values = rev(c(cb_pal[1], cb_pal[4], cb_pal[8]))) +
  labs(title = "Some or a lot of trust in different sources of news, by language spoken at home", x = NULL, y = NULL)
```

Pretty similar between foreign-born and US-born Latinos.

```{r latinopob_trust}
latinopob_trust <- trust %>% 
  filter(category == "latino_by_pob", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, level, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "level"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(`Some or a lot`, `Not at all`)) %>% 
  pivot_longer(cols = c("Some or a lot", "Not at all", "Total"), names_to = "response", values_to = "n") %>%
  mutate(response = as.factor(response) %>% fct_relevel(., "Some or a lot", "Not at all")) %>% 
  group_by(category, group, level) %>% 
  calc_shares(group = response, denom = "Total", value = n)

latinopob_trust %>% 
  filter(response == "Some or a lot", group != "Not Latino") %>% 
  ggplot(aes(x = share, y = reorder(level, share), group = group)) +
  geom_col(aes(fill = group), width = .8, position = position_dodge(.9)) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, position = position_dodge(.9)) +
  theme(legend.position = "bottom", axis.text.x = element_blank()) +
  guides(fill = guide_legend(title = NULL, rev = T)) +
  scale_fill_manual(values = rev(c(cb_pal[1], cb_pal[4]))) +
  labs(title = "Some or a lot of trust in different sources of news, by place of birth", x = NULL, y = NULL)
```

## Beliefs

```{r make_believe}
beliefs_all <- read %>% 
  select(trust_sources_of_news_about_my_community, local_news_covers_issues_important_to_me, local_news_reflects_my_beliefs_and_values) %>% 
  mutate(category = "total", group = "total") %>% 
  pivot_longer(cols = c("trust_sources_of_news_about_my_community", "local_news_covers_issues_important_to_me", "local_news_reflects_my_beliefs_and_values"), names_to = "question", values_to = "response") %>% 
   mutate(question = str_replace_all(question, "_", " "),
         question = str_replace(question, "trust", "I trust"),
         question = str_to_sentence(question))

beliefs <- read %>% 
  filter(latino == "Yes") %>% 
  select(age, gender, language, latino_by_pob, trust_sources_of_news_about_my_community, local_news_covers_issues_important_to_me, local_news_reflects_my_beliefs_and_values) %>% 
  pivot_longer(cols = c("trust_sources_of_news_about_my_community", "local_news_covers_issues_important_to_me", "local_news_reflects_my_beliefs_and_values"), names_to = "question", values_to = "response") %>%
  mutate(question = str_replace_all(question, "_", " "),
         question = str_replace(question, "trust", "I trust"),
         question = str_to_sentence(question)) %>% 
  pivot_longer(cols = age:latino_by_pob, names_to = "category", values_to = "group") %>% 
  bind_rows(beliefs_all)
```

```{r beliefs_total}
beliefs_total <- beliefs %>% 
  filter(category == "total", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, question, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "question"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(Neutral, Agree, Disagree)) %>% 
  pivot_longer(cols = c("Neutral", "Agree", "Disagree", "Total"), names_to = "response", values_to = "n") %>%
  group_by(category, group, question) %>% 
  calc_shares(group = response, denom = "Total", value = n) %>% 
  ungroup() %>% 
  mutate(response = as.factor(response) %>% fct_relevel(., "Agree", "Neutral", "Disagree"))


beliefs_total %>% 
  mutate(response = fct_rev(response)) %>% 
  mutate(question = str_wrap(question, 26)) %>% 
  filter(response == "Agree") %>% 
  ggplot(aes(x = share, y = reorder(question, share))) +
  geom_col(width = .8) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  theme(legend.position = "none",
        axis.text.x = element_blank()) +
  labs(title = "Share of respondents who agree with statements about local news", x = NULL, y = NULL)
```


Most older adults believe the news covers important topics and they trust the sources of news they get, but there's a lot of ambivalence about whether news reflects their values, although a plurality of older adults agree with that. We see this in our DCWS survey data, too... older adults just think more stuff is relevant to them.

```{r beliefs_age}
age_beliefs <- beliefs %>% 
  filter(category == "age", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, question, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "question"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(Neutral, Agree, Disagree)) %>% 
  pivot_longer(cols = c("Neutral", "Agree", "Disagree", "Total"), names_to = "response", values_to = "n") %>%
  group_by(category, group, question) %>% 
  calc_shares(group = response, denom = "Total", value = n) %>% 
  ungroup() %>% 
  mutate(response = as.factor(response) %>% fct_relevel(., "Agree", "Neutral", "Disagree"))

age_beliefs %>% 
  left_join(age_labels, by = c("group" = "age")) %>% 
  mutate(response = fct_rev(response), label = fct_rev(label)) %>% 
  mutate(question = str_wrap(question, 26)) %>% 
  filter(response == "Agree") %>% 
  ggplot(aes(x = share, y = question, group = label)) +
  geom_col(aes(fill = label), width = .8, position = position_dodge(.9)) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = "black", position = position_dodge(.9)) +
  geom_text(data = . %>% filter(label == "30-49"), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, position = position_dodge(.9)) +
  theme(legend.position = "bottom", axis.text.x = element_blank()) +
  guides(fill = guide_legend(title = NULL, rev = T)) +
  scale_fill_manual(values = rev(c(cb_pal[1], cb_pal[4], cb_pal[8]))) +
  labs(title = "Share of respondents who agree with statements about local news, by age", x = NULL, y = NULL)

```


```{r beliefs_gender}
gender_beliefs <- beliefs %>% 
  filter(category == "gender", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, question, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "question"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(Neutral, Agree, Disagree)) %>% 
  pivot_longer(cols = c("Neutral", "Agree", "Disagree", "Total"), names_to = "response", values_to = "n") %>%
  group_by(category, group, question) %>% 
  calc_shares(group = response, denom = "Total", value = n) %>% 
  ungroup() %>% 
  mutate(response = as.factor(response) %>% fct_relevel(., "Agree", "Neutral", "Disagree"))

gender_beliefs %>% 
  filter(group != "Transgender & NB") %>% 
  mutate(question = str_wrap(question, 26)) %>% 
  filter(response == "Agree") %>% 
  ggplot(aes(x = share, y = question, group = group)) +
  geom_col(aes(fill = group), width = .8, position = position_dodge(.9)) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, position = position_dodge(.9)) +
  theme(legend.position = "bottom", axis.text.x = element_blank()) +
  guides(fill = guide_legend(title = NULL, rev = T)) +
  scale_fill_manual(values = (c(cb_pal[1], cb_pal[4]))) +
  labs(title = "Share of respondents who agree with statements about local news, by gender", x = NULL, y = NULL)
```

People who speak Spanish at home are more likely to agree that local news reflects their beliefs. I wonder if this is influenced by the fact people are answering this survey for their local paper.

```{r beliefs_lang}
lang_beliefs <- beliefs %>% 
  filter(category == "language", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, question, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "question"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(Neutral, Agree, Disagree)) %>% 
  pivot_longer(cols = c("Neutral", "Agree", "Disagree", "Total"), names_to = "response", values_to = "n") %>%
  group_by(category, group, question) %>% 
  calc_shares(group = response, denom = "Total", value = n) %>% 
  ungroup() %>% 
  mutate(response = as.factor(response) %>% fct_relevel(., "Agree", "Neutral", "Disagree"))

lang_beliefs %>% 
  filter(response == "Agree") %>% 
  mutate(question = str_wrap(question, 20)) %>% 
  mutate(group = as.factor(group),
         group = fct_rev(group)) %>% 
  ggplot(aes(x = share, y = question, group = group)) +
  geom_col(aes(fill = group), width = .8, position = position_dodge(.9)) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = "black", position = position_dodge(.9)) +
  geom_text(data = . %>% filter(group == "English"), aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, position = position_dodge(.9)) +
  theme(legend.position = "bottom", axis.text.x = element_blank()) +
  guides(fill = guide_legend(title = NULL, rev = T)) +
  scale_fill_manual(values = rev(c(cb_pal[1], cb_pal[4], cb_pal[8]))) +
  labs(title = "Share of respondents who agree with statements about local news, by language spoken at home", x = NULL, y = NULL)
```

Again, pretty similar here.

```{r beliefs_latinopob}
latinopob_beliefs <- beliefs %>% 
  filter(category == "latino_by_pob", !is.na(group), !is.na(response)) %>% 
  group_by(category, group, question, response) %>% 
  count() %>% 
  pivot_wider(id_cols = c("category", "group", "question"), names_from = "response", values_from = "n") %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(Total = sum(Neutral, Agree, Disagree)) %>% 
  pivot_longer(cols = c("Neutral", "Agree", "Disagree", "Total"), names_to = "response", values_to = "n") %>%
  group_by(category, group, question) %>% 
  calc_shares(group = response, denom = "Total", value = n) %>% 
  ungroup() %>% 
  mutate(response = as.factor(response) %>% fct_relevel(., "Agree", "Neutral", "Disagree"))

latinopob_beliefs %>% 
  filter(group != "Not Latino") %>% 
  mutate(question = str_wrap(question, 26)) %>% 
  filter(response == "Agree") %>% 
  ggplot(aes(x = share, y = question, group = group)) +
  geom_col(aes(fill = group), width = .8, position = position_dodge(.9)) +
  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), hjust = 1.2, color = label_col, position = position_dodge(.9)) +
  theme(legend.position = "bottom", axis.text.x = element_blank()) +
  guides(fill = guide_legend(title = NULL, rev = T)) +
  scale_fill_manual(values = rev(c(cb_pal[1], cb_pal[4]))) +
  labs(title = "Share of respondents who agree with statements about local news, by place of birth", x = NULL, y = NULL)
```
